\documentclass[11pt]{amsart}
\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage[margin=1.15in]{geometry}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{enumitem}
\hypersetup{colorlinks=true, linkcolor=blue!55!black, citecolor=blue!55!black,
  urlcolor=blue!55!black}
% ---------- theorem environments ----------
\theoremstyle{plain}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{assumption}[theorem]{Assumption}
\newtheorem{hypothesis}[theorem]{Hypothesis}
\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}
% ---------- macros ----------
\newcommand{\R}{\mathbb{R}}
\newcommand{\fpl}[1]{(-\Delta_p)^{s}#1}
\newcommand{\Jp}[1]{|#1|^{p-2}#1}
\newcommand{\al}{\alpha}
\newcommand{\asp}{\alpha_{s,p}}
\newcommand{\Tail}{\mathrm{Tail}_{p-1,sp}}
\newcommand{\fint}{\mathop{\ooalign{$\displaystyle\int$\cr\hidewidth\raise.5ex\hbox{$\scriptstyle-$}\hidewidth}}}

\title[A nonlocal two-phase $p$-dead-core problem]{Improved growth at branching
points for a two-phase nonlocal dead-core problem driven by the fractional
$p$-Laplacian: a conditional analysis}
\author{Hikmatullo Ismatov}
\address{King Abdullah University of Science and Technology (KAUST)}
\email{hikmatullo.ismatov@kaust.edu.sa}
\date{\today}

\begin{document}
\begin{abstract}
We study the two-phase nonlocal dead-core problem
$\fpl{u}=u_+^{\gamma}-u_-^{\gamma}$ governed by the fractional $p$-Laplacian,
with $0<\gamma<p-1$, $s\in(0,1)$ and $p\ge2$. The natural scaling predicts the
improved growth $|u(x)|\le C|x-x_0|^{\beta}$, $\beta=\frac{sp}{p-1-\gamma}$, at
flat branching points. We carry out an honest analysis of the blow-up
strategy. The scaling identity and the disappearance of the absorption term
along the amplified blow-up are unconditional. We show that direct compactness
of the normalized blow-ups is \emph{obstructed} by a tail blow-up, and that the
first increments of an entire $(s,p)$-harmonic function solve a \emph{linear}
nonlocal equation; the existing regularity theory (Brasco--Lindgren--Schikorra,
Giovagnoli--Jesus--Silvestre) provides \emph{local} H\"older estimates for this
linearized equation but \emph{not} the global, scale-uniform Liouville theorem
that the argument needs. Accordingly we state the growth estimate
\emph{conditionally}, isolating the missing linearized Liouville input, the
compactness/tail control, and the inhomogeneous $C^{1}$-regularity required to
make sense of flatness. We also record the admissible parameter range for the
increment route and note that, for $p\neq2$, the usable cap is
$\beta<1+\asp$, not $\beta<2$.
\end{abstract}
\maketitle

%======================================================================
\section{Introduction}\label{sec:intro}
%======================================================================
We study the two-phase nonlocal problem
\begin{equation}\label{eq:main}
  \fpl{u}=u_+^{\gamma}-u_-^{\gamma}\qquad\text{in }B_1\subset\R^n,
\end{equation}
where $\fpl{}$ is the fractional $p$-Laplacian (Section~\ref{sec:prelim}),
$0<\gamma<p-1$, $s\in(0,1)$ and $p\ge2$. Such equations model diffusion in
the presence of a strong absorption: when the reaction order $\gamma$ is
sublinear, the solution may vanish on a whole interior region, the
\emph{dead core}, on whose boundary $u$ touches zero together with its
gradient. The non-Lipschitz character of $u\mapsto u^{\gamma}$ at the origin
is what permits dead cores to form.

Two features distinguish \eqref{eq:main} from the classical theory. It is
\emph{nonlocal}: $\fpl{u}(x)$ depends on $u$ over all of $\R^n$, so the
maximum-principle techniques of the local one-phase theory are unavailable.
And it is \emph{two-phase}: $u$ is not sign-constrained, so the points where
it touches zero need not be extrema. The one-phase signed problem is, in
addition, obstructed nonlocally by the strong minimum principle, which makes
the two-phase formulation \eqref{eq:main} the natural setting.

The exponent dictated by the scaling of \eqref{eq:main}
(Proposition~\ref{prop:scaling}) is
\begin{equation}\label{eq:beta}
  \beta:=\frac{sp}{\,p-1-\gamma\,},
\end{equation}
the analogue of $\frac{2s}{1-\gamma}$ in the fractional Laplacian case
$p=2$ of dos Prazeres, Teymurazyan and Urbano~\cite{PTU}.

\subsection{Strategy and the present obstruction}
The general regularity theory of the fractional $p$-Laplacian provides a
baseline regularity scale for solutions of \eqref{eq:main}: by Biswas and
Topp~\cite{BT} bounded solutions are $C^{0,\gamma_\circ}$ with
$\gamma_\circ=\min\{1,\frac{sp}{p-1}\}$, hence locally Lipschitz when
$\frac{sp}{p-1}>1$. The free-boundary scaling \eqref{eq:beta} predicts a
\emph{better} exponent $\beta$ at branching points, and the natural route to it
is a blow-up argument: rescale $u$ around the branching point, show the
absorption term vanishes in the limit, and classify the limit by a
Liouville-type theorem. This is the scheme of~\cite{PTU} for $p=2$ and of
Correa--dos Prazeres~\cite{CP} for the local $p$-Laplacian.

Unlike those settings, the nonlinear \emph{nonlocal} operator creates two
serious difficulties that this paper isolates rather than hides.
\begin{enumerate}[leftmargin=2em]
\item \emph{Compactness/tails.} Interior H\"older estimates for $\fpl{}$ carry
nonlocal tail terms. We show (Proposition~\ref{prop:tailobstruction}) that the
naturally normalized blow-up sequence has a \emph{divergent} tail, so its
compactness does \emph{not} follow from local $L^\infty$ bounds alone.
\item \emph{Nonlinearity in the Liouville step.} For $p\neq2$ differences of
solutions are not solutions, so the linear-nonlocal Liouville theorem
of~\cite{PTU} cannot be copied. We observe that first increments solve a
\emph{linear} nonlocal equation (Proposition~\ref{prop:linincr}); the
literature~\cite{BLS,GJS} gives \emph{local} H\"older regularity for that
equation, but the \emph{global, scale-uniform} Liouville theorem the argument
needs is not available and is isolated here as a hypothesis~$(\star)$.
\end{enumerate}
Consequently we state the growth estimate as a \emph{conditional} theorem
(Theorem~\ref{thm:growth}), with all missing analytic inputs collected in
Section~\ref{sec:open}.

\subsection{What ``improved regularity'' should mean}
For $p=2$ the comparison is clean: once $u$ is Lipschitz the right-hand side
of $-(-\Delta)^s u=u_+^\gamma-u_-^\gamma$ is $C^\gamma$, Schauder theory gives
the baseline $C^{2s+\gamma}$, and $\frac{2s}{1-\gamma}$ exceeds it for
$s>\tfrac12$. For the fractional $p$-Laplacian the operator is nonlinear and
degenerate, and a Schauder statement $f\in C^\gamma\Rightarrow u\in
C^{sp+\gamma}$ for $\fpl{u}=f$ is \emph{not} among the inputs currently
available (see Remark~\ref{rem:baseline}). We therefore keep two exponents
separate. The scaling exponent $\beta$ is unconditional. A \emph{formal}
Schauder baseline $sp+\gamma$, treating the operator as of order $sp$, makes
the estimate a genuine improvement precisely when
\begin{equation}\label{eq:improve}
  \frac{sp}{p-1-\gamma}>sp+\gamma
  \quad\Longleftrightarrow\quad
  \gamma^2+(sp-(p-1))\gamma+sp(2-p)>0 .
\end{equation}
For $p=2$ this reads $\gamma^2+(2s-1)\gamma>0$, valid for all $\gamma>0$ when
$s>\tfrac12$; for $p>2$ it becomes $\gamma>\gamma_S$ with
$\gamma_S=\frac{(p-1)-sp+\sqrt{(sp-(p-1))^2+4sp(p-2)}}{2}$.
The third relevant exponent is $1+\asp$, where $\asp=\asp(n)\in(0,1)$ is the
H\"older exponent furnished by the regularity theory for the linearized
increment equation (Section~\ref{sec:liouville}). It is \emph{not} a Schauder
baseline but the threshold of the Liouville step, which requires
$\beta<1+\asp$.

\subsection{The admissible parameter range for the increment route}
The increment route (Section~\ref{sec:liouville}) carries, besides $0<\gamma<p-1$,
two constraints: a tail condition and the Liouville cap. The tail condition is
\begin{equation}\label{eq:tailcond}
  \beta(p-1)<sp+1
  \qquad\Longleftrightarrow\qquad
  \boxed{\ \gamma<\frac{p-1}{1+sp}\ }
\end{equation}
(see Remark~\ref{rem:tailcond}), and the Liouville cap is $\beta<1+\asp$. We
work in the range of~\cite{GJS},
\begin{equation}\label{eq:gjs-range}
  p\ge2,\qquad p<\frac{2}{1-s}\quad\Longleftrightarrow\quad s>1-\frac2p,
\end{equation}
which is exactly the range in which the linearized operator is elliptic of
positive order $sp-p+2$ (Remark~\ref{rem:order}). For a cleaner first theorem
we may further restrict to the Lipschitz regime
\begin{equation}\label{eq:lip-range}
  sp>p-1\quad\Longleftrightarrow\quad s>1-\frac1p,
\end{equation}
in which $\beta>1$ is automatic and the flat branching condition is
meaningful. The clean hypothesis block is then
\begin{equation}\label{eq:hyp-block}
  p\ge2,\qquad s>1-\frac1p,\qquad p<\frac{2}{1-s},\qquad
  0<\gamma<\frac{p-1}{1+sp},\qquad \frac{sp}{p-1-\gamma}<1+\asp .
\end{equation}
A direct computation (Remark~\ref{rem:nonempty}) shows that, with the cap
written either as $\beta<2$ or as $\beta<1+\asp$ for any $\asp>0$, the
resulting $\gamma$-range is nonempty \emph{if and only if} $p<\frac2{1-s}$; and
at $p=2$ the tail condition \eqref{eq:tailcond} reduces to PTU's
$\gamma<\frac1{1+2s}$.

\subsection{Main result}
The robust part of the argument is unconditional
(Propositions~\ref{prop:scaling}, \ref{prop:homog}, \ref{prop:linincr}); the
growth estimate is conditional.

\begin{theorem}[Conditional growth estimate; informal]\label{thm:main-intro}
Assume \eqref{eq:hyp-block}, the compactness/admissibility
Assumption~\ref{ass:compact}, and the linearized Liouville
input~$(\star)$ of Theorem~\ref{thm:liouville-incr}. Let $u\in L^\infty(\R^n)$
solve \eqref{eq:main} with $0$ a flat branching point
(Definition~\ref{def:branch}). Then $|u(x)|\le C|x|^{\beta}$ for $x\in B_{1/2}$,
with $C=C(n,s,p,\gamma)$.
\end{theorem}

Letting $s\nearrow1$ \emph{formally} yields the analogous estimate for the
local two-phase problem $\Delta_p u=u_+^\gamma-u_-^\gamma$ with exponent
$\frac{p}{p-1-\gamma}$ (Section~\ref{sec:consequences}), which does not appear
to be recorded in the literature; this limit is itself conditional, as the
constants of~\cite{GJS} are not uniform as $s\to1$.

\medskip
\noindent\textbf{Organization.} Section~\ref{sec:prelim} fixes notation, the
notion of solution, the scaling and homogeneity identities, the increment
linearization, the regularity inputs, and the tail obstruction.
Section~\ref{sec:liouville} treats the Liouville step, both the conditional
direct form and the conditional increment form. Section~\ref{sec:growth} proves
the conditional growth theorem. Section~\ref{sec:consequences} collects
consequences, and Section~\ref{sec:open} lists the remaining analytic inputs.

%======================================================================
\section{Preliminaries}\label{sec:prelim}
%======================================================================

\subsection{Notation and the operator}
$B_r(x_0)$ is the open ball of radius $r$ at $x_0$, $B_r:=B_r(0)$, and
$u_\pm:=\max\{\pm u,0\}$. With $J_p(t):=\Jp{t}$,
\[
  \fpl{u}(x):=\mathrm{P.V.}\!\int_{\R^n}
    \frac{J_p\big(u(x)-u(y)\big)}{|x-y|^{n+sp}}\,dy,
\]
the normalizing constant being omitted. The nonlocal tail is
\[
  \Tail(u;x_0,R):=\Big(R^{sp}\!\int_{\R^n\setminus B_R(x_0)}
    \frac{|u(y)|^{p-1}}{|y-x_0|^{n+sp}}\,dy\Big)^{\!\frac{1}{p-1}}.
\]
Solutions of \eqref{eq:main} are taken in the weak sense, with
$u\in W^{s,p}_{loc}\cap L^\infty(\R^n)$ and finite tail; weak and viscosity
solutions coincide~\cite{KKL}.

\subsection{Scaling and homogeneity}
\begin{proposition}[Scaling]\label{prop:scaling}
For $A>0$, $r>0$ and $v(x):=u(rx)/A$,
\[
  \fpl{v}(x)=A^{1-p}\,r^{\,sp}\,(\fpl{u})(rx).
\]
In particular, for $u_r(x):=u(rx)/r^{\beta}$ (i.e.\ $A=r^{\beta}$),
$\fpl{u_r}(x)=r^{\,sp-\beta(p-1)}(\fpl{u})(rx)$, and $u_r$ solves
\eqref{eq:main} in $B_{1/r}$ if and only if $sp-\beta(p-1)+\beta\gamma=0$, i.e.\
$\beta=\frac{sp}{p-1-\gamma}$.
\end{proposition}
\begin{proof}
Since $v(x)-v(y)=A^{-1}(u(rx)-u(ry))$ and $J_p$ is $(p-1)$-homogeneous,
$\fpl{v}(x)=A^{1-p}\mathrm{P.V.}\!\int J_p(u(rx)-u(ry))|x-y|^{-n-sp}\,dy$; the
substitution $z=ry$ contributes $r^{sp}$, giving the first identity. Taking
$A=r^{\beta}$ and using $(u_r)_\pm=r^{-\beta}u_\pm(r\cdot)$, the right-hand side
of \eqref{eq:main} scales by $r^{-\beta\gamma}$; balancing the powers of $r$
gives \eqref{eq:beta}.
\end{proof}

\begin{proposition}[Amplified blow-up: vanishing right-hand side]\label{prop:homog}
Let $u_k$ solve \eqref{eq:main} with $\|u_k\|_{L^\infty}\le M$, let $r_k\to0$,
$\theta_k\to\infty$, and
\[
  \theta_k=\frac{\sup_{B_{r_k}}|u_k|}{r_k^{\beta}},\qquad
  v_k(x):=\frac{u_k(r_kx)}{\theta_k r_k^{\beta}}.
\]
Then
\[
  \fpl{v_k}=\theta_k^{\,\gamma-(p-1)}
   \big[(v_k)_+^{\gamma}-(v_k)_-^{\gamma}\big]\quad\text{in }B_{1/r_k},
\]
and since $\gamma<p-1$ the coefficient $\theta_k^{\gamma-(p-1)}\to0$, so the
absorption term vanishes in the limit. We do \emph{not} conclude that a limit
$v_0$ is $(s,p)$-harmonic in the standard sense; see
Remark~\ref{rem:renorm}.
\end{proposition}
\begin{proof}
With $A=\theta_k r_k^\beta$, Proposition~\ref{prop:scaling} gives
$\fpl{v_k}=(\theta_k r_k^\beta)^{1-p}r_k^{sp}(\fpl{u_k})(r_k\cdot)$. Inserting
the equation and $(v_k)_\pm=(\theta_kr_k^\beta)^{-1}(u_k)_\pm(r_k\cdot)$
produces the factor $(\theta_kr_k^\beta)^{\gamma-(p-1)}r_k^{sp}
=\theta_k^{\gamma-(p-1)}$, since $\beta(p-1-\gamma)=sp$. The passage to the
limit requires a stability statement for $\fpl{}$ under local uniform
convergence \emph{with tail control}; the latter is not automatic
(Proposition~\ref{prop:tailobstruction}) and is part of
Assumption~\ref{ass:compact}.
\end{proof}

\begin{remark}[The limiting equation must be renormalized]\label{rem:renorm}
The expected growth $|v_0(x)|\lesssim|x|^{\beta}$ has $\beta(p-1)>sp$, so $v_0$
need not lie in the tail space $L^{p-1}_{sp}(\R^n)$ on which $\fpl{v_0}$ is
defined; thus ``$\fpl{v_0}=0$'' is \emph{not} literally well-posed. This
already occurs for $p=2$ in~\cite{PTU}, where the limit is handled only through
its increments: $(-\Delta)^s\big(v_0(\cdot+h)-v_0\big)=0$, which is well defined
because increments grow one order slower. We adopt the same convention: the
limiting statement is the \emph{increment} equation $L_{K}w_0^h=0$
(Proposition~\ref{prop:linincr}), meaningful under the tail
condition~\eqref{eq:tailcond}. A rigorous framework for this is the notion of
Dipierro--Savin--Valdinoci~\cite{DSV} of solutions of polynomial growth, in
which the equation is read \emph{modulo polynomials}: a constant (or affine)
right-hand side is identified with $0$. For $p=2$ this makes precise the
second-difference cancellation of~\cite{PTU}. For $p\neq2$, however, the
increment kernel is variable, degenerate and non-translation-invariant, and
\cite{DSV} (stated for the fractional Laplacian) does not cover it; the
corresponding modulo-polynomial theory for $L_{K_h}$ is an open analytic input
(Section~\ref{sec:open}).
\end{remark}

\subsection{Increments solve a linear equation}
\begin{proposition}[Linearization along increments]\label{prop:linincr}
For $v\in C^1_{loc}\cap L^\infty_{loc}$ and $h\in\R^n$, set $w^h:=v(\cdot+h)-v$.
Then, in the weak sense, for every $\varphi\in C^\infty_c(\R^n)$,
\[
  \iint_{\R^n\times\R^n}\big(w^h(x)-w^h(y)\big)\big(\varphi(x)-\varphi(y)\big)
   \frac{K_h(x,y)}{|x-y|^{n+sp}}\,dx\,dy
   = \langle\fpl{[v(\cdot+h)]}-\fpl{v},\varphi\rangle,
\]
with the \emph{symmetric, nonnegative} kernel
\[
  K_h(x,y)=(p-1)\int_0^1\big|(1-t)(v(x)-v(y))+t\,(v(x+h)-v(y+h))\big|^{p-2}dt .
\]
In particular, if $v$ is $(s,p)$-harmonic then $w^h$ is a weak solution of the
\emph{linear} nonlocal equation $L_{K_h}w^h=0$ --- though not of the
homogeneous fractional $p$-Laplacian.
\end{proposition}
\begin{proof}
Since $\fpl{}$ is translation invariant, $V:=v(\cdot+h)$ is $(s,p)$-harmonic
whenever $v$ is. Subtracting the weak formulations of $V$ and $v$ tested
against $\varphi$, and using the identity (valid for $p\ge2$, where $J_p\in
C^1$)
\[
  J_p(b)-J_p(a)=(p-1)\Big(\int_0^1|a+t(b-a)|^{p-2}dt\Big)(b-a),\quad
  a=v(x)-v(y),\ b=V(x)-V(y),
\]
with $b-a=w^h(x)-w^h(y)$, yields the displayed bilinear identity.
\end{proof}

\begin{corollary}[Weak increment identity for the blow-up sequence]
\label{cor:incr-weak}
Let $v_k$ solve $\fpl{v_k}=\theta_k^{\gamma-(p-1)}\Phi(v_k)$ weakly in
$B_{\rho_k}$, $\rho_k:=1/r_k$, with $\Phi(t)=t_+^{\gamma}-t_-^{\gamma}$, and fix
$h\in\R^n$, $|h|<\rho_k/4$. Set $W_k^h:=v_k(\cdot+h)-v_k$ and let
\[
  \Omega_k^h:=\{x\in\R^n:\ x\in B_{\rho_k}\text{ and }x+h\in B_{\rho_k}\}
  \supset B_{\rho_k/2}
\]
be the common admissible domain. Then for every
$\varphi\in C_c^\infty(\Omega_k^h)$,
\begin{equation}\label{eq:weak-incr-full}
  \frac12\iint_{\R^n\times\R^n}
   a_k^h(x,y)\,
   \frac{\big(W_k^h(x)-W_k^h(y)\big)\big(\varphi(x)-\varphi(y)\big)}
        {|x-y|^{n+sp}}\;dx\,dy
  \;=\;\int_{\R^n} f_k^h\,\varphi\,dx,
\end{equation}
with
\[
  a_k^h(x,y)=(p-1)\int_0^1\big|B_k(x,y)+t\big(A_k(x,y)-B_k(x,y)\big)\big|^{p-2}dt,
  \qquad
  \begin{aligned}
   A_k(x,y)&=v_k(x+h)-v_k(y+h),\\
   B_k(x,y)&=v_k(x)-v_k(y),
  \end{aligned}
\]
and
\[
  f_k^h:=\theta_k^{\gamma-(p-1)}\big[\Phi\big(v_k(\cdot+h)\big)-\Phi(v_k)\big].
\]
Moreover $f_k^h\to0$ in $L^\infty_{loc}$: on any fixed ball $B_R$ where
$\sup_k\|v_k\|_{L^\infty(B_{R+|h|})}\le C_R$,
\[
  \|f_k^h\|_{L^\infty(B_R)}
  \le 2\,\theta_k^{\gamma-(p-1)}\,C_R^{\gamma}\ \longrightarrow\ 0
  \qquad(k\to\infty),
\]
since $\gamma<p-1$ and $\theta_k\to\infty$.
\end{corollary}
\begin{proof}
Test the weak formulation of the equation for $v_k(\cdot+h)$ (valid in
$B_{\rho_k}-h\supset\Omega_k^h$, by translating the formulation for $v_k$)
and that for $v_k$ against the same $\varphi\in C_c^\infty(\Omega_k^h)$, and
subtract. On the left, apply the identity of
Proposition~\ref{prop:linincr} pointwise in $(x,y)$ (legitimate for $p\ge2$,
where $J_p\in C^1(\R)$, by the fundamental theorem of calculus); the symmetric
$\frac12\iint$ normalization matches the convention in
\eqref{eq:weak-incr-full}. Every integral converges absolutely: near the
diagonal, $a_k^h(x,y)\le(p-1)(|A_k|+|B_k|)^{p-2}\lesssim|x-y|^{p-2}$ by the
local Lipschitz bound for $v_k$, so the integrand is
$O(|x-y|^{p-n-sp})$ with $p>sp$; in the far field, the tail hypotheses of
\S\ref{ssec:truncdiff} apply. On the right, $|\Phi(a)-\Phi(b)|\le
2\max(|a|,|b|)^{\gamma}$ for $0<\gamma\le1$ (and
$\le\gamma\max(|a|,|b|)^{\gamma-1}|a-b|$ for $\gamma\ge1$), giving the stated
$L^\infty_{loc}$ bound and the convergence $f_k^h\to0$.
\end{proof}

\begin{remark}[Degeneracy and order of the linearized kernel]\label{rem:order}
When $v$ is differentiable, $K_h(x,y)\sim(p-1)|Dv(x)|^{p-2}|x-y|^{p-2}$ near
the diagonal, so $K_h(x,y)|x-y|^{-n-sp}$ is of homogeneity $-n-(sp-(p-2))$:
the linearized operator $L_{K_h}$ has order $sp-p+2$, positive precisely when
$s>1-\frac2p$, i.e.\ in the range \eqref{eq:gjs-range}. For $p>2$ the weight
$|Dv|^{p-2}$ \emph{vanishes where $Dv=0$} and grows in the far field; thus
$L_{K_h}$ is \emph{degenerate} at critical points of $v$ and is not uniformly
elliptic globally. This is a serious issue here, because the blow-up limit is
flat at the origin in the sup sense ($\sup_{B_r}|v_0|=o(r)$ along the
normalization; the pointwise statement $Dv_0(0)=0$ would require the
$C^1_{loc}$-compactness of Assumption~\ref{ass:compact} and is not asserted
unconditionally), exactly where the kernel degenerates.

\emph{Warning (three exponents, not one).} The coefficient $K_h$ scales
differently in three regimes and these must not be conflated:
\begin{itemize}[leftmargin=2em]
\item \emph{near-diagonal:} $K_h\sim|Dv(x)|^{p-2}|x-y|^{p-2}$ --- governs the
  \emph{order} $sp-p+2$ of $L_{K_h}$;
\item \emph{near a flat point:} the weight $|Dv(x)|^{p-2}\sim
  |x|^{(\beta-1)(p-2)}$ --- governs the \emph{degeneracy at the origin}
  (route~(W) of \S\ref{sec:open});
\item \emph{far field:} $K_h(x,y)\sim|v(y)|^{p-2}\sim|y|^{\beta(p-2)}$ for
  $x$ in a fixed ball and $|y|\to\infty$ --- the coefficient sees the
  \emph{function values}, not the increments; this exponent, and not
  $(\beta-1)(p-2)$, is the one entering the tail condition
  \eqref{eq:tailcond}.
\end{itemize}
\end{remark}

\subsection{Regularity inputs}
We record the two regularity facts we use. Both are \emph{local}.

\begin{lemma}[Inhomogeneous H\"older/Lipschitz baseline~\cite{BT}]\label{lem:bt}
Let $p>1$, $s\in(0,1)$ and let $u$ be a bounded weak solution of $\fpl{u}=f$
in $B_2$ with $f\in L^\infty(B_2)$ and $\frac{sp}{p-1}\neq1$. Then
$u\in C^{0,\gamma_\circ}_{loc}(B_2)$ with
$\gamma_\circ=\min\{1,\frac{sp}{p-1}\}$; in particular $u$ is locally Lipschitz
when $\frac{sp}{p-1}>1$.
\end{lemma}

\begin{lemma}[Homogeneous $C^{1,\al_0}$ estimate and local linearized regularity~\cite{GJS}]\label{lem:gjs}
Let $2\le p<\frac{2}{1-s}$. If $v$ is $(s,p)$-harmonic in $B_2$ with
$\Tail(v;0,2)<\infty$, then $v\in C^{1,\al_0}(B_1)$ for some
$\al_0=\al_0(n,s,p)\in(0,1)$, with
$\|v\|_{C^{1,\al_0}(B_1)}\le C(\|v\|_{L^\infty(B_2)}+\Tail(v;0,2))$.
Moreover~\cite[\S7]{GJS} establishes a \emph{local} interior H\"older estimate
$[w]_{C^{\asp}(B_{1/2})}\le C(\|w\|_{L^\infty(\R^n)}+\|f\|_{L^\infty(B_1)})$ for
weak solutions of the linear equation $L_K w=f$ with a measurable kernel $K$
satisfying symmetry, a scaled upper bound, and a coercivity (ellipticity)
hypothesis --- the latter requiring the kernel to be \emph{nondegenerate}.
\end{lemma}

\begin{remark}[The Schauder baseline; flatness is conditional]\label{rem:baseline}
Lemma~\ref{lem:bt} is the best presently available regularity for solutions of
\eqref{eq:main}: $C^{0,\gamma_\circ}$, and Lipschitz exactly when
$\frac{sp}{p-1}>1$. A Schauder statement $f\in C^\gamma\Rightarrow u\in
C^{sp+\gamma}$, or even an \emph{inhomogeneous} $C^{1,\sigma}$ estimate for
$\fpl{u}=f\in L^\infty$, is \emph{not} available from~\cite{BT,GJS}.
Consequently two things are conditional and must be flagged. First, the
comparison \eqref{eq:improve} is against a \emph{formal} baseline. Second, the
condition $Du(x_0)=0$ in the definition of a flat branching point presupposes
$C^1$-regularity of $u$, which we do \emph{not} have for the inhomogeneous
equation; see Definition~\ref{def:branch}. Whether inhomogeneous fractional
$p$-Poisson regularity (e.g.\ B\"ogelein--Duzaar--Liao--Moring~\cite{BDLM})
upgrades Lemma~\ref{lem:bt} to a genuine interior $C^{1,\al}$ estimate, thereby
licensing $Du(x_0)=0$ and the $C^{1,\al'}$ blow-up device, is an open input
(Section~\ref{sec:open}).
\end{remark}

\subsection{The tail obstruction to compactness}
\begin{proposition}[Tail blow-up of the normalized sequence]\label{prop:tailobstruction}
Let $u_k$, $r_k$, $\theta_k$, $v_k$ be as in Proposition~\ref{prop:homog}, with
$\|u_k\|_{L^\infty(\R^n)}\le M$, and set $\varepsilon_k:=\sup_{B_{r_k}}|u_k|
=\theta_k r_k^{\beta}$, so that $v_k(y)=u_k(r_ky)/\varepsilon_k$. Then:
\begin{enumerate}[leftmargin=2em]
\item $|v_k(y)|\le M/\varepsilon_k$ for all $y\in\R^n$;
\item if $0$ is a branching point and the $u_k$ are uniformly Lipschitz near
$0$ \textnormal{(Lemma~\ref{lem:bt}, $\frac{sp}{p-1}>1$)}, then
$\varepsilon_k\to0$, and the \emph{available} upper bounds
$|v_k(y)|\le\min\{C|y|^\beta,\,M/\varepsilon_k\}$ yield only
\[
  \Tail(v_k;0,R)^{\,p-1}\ \lesssim\ C(R,n,s,p)\,\varepsilon_k^{-\gamma},
\]
a bound that diverges as $k\to\infty$; in particular these bounds furnish
\emph{no} uniform-in-$k$ tail control.
\end{enumerate}
\end{proposition}
\begin{proof}
(1) is immediate from $|u_k|\le M$. For (2): at a branching point with
$u_k(0)=0$ and uniform Lipschitz bound $L$, $\varepsilon_k\le Lr_k\to0$. Split
the tail of $v_k$ at the crossover $\rho_k=(M/C\varepsilon_k)^{1/\beta}$ of the
two bounds $|v_k|\le C|y|^\beta$ and $|v_k|\le M/\varepsilon_k$; using
$\beta(p-1)-sp=\frac{\gamma sp}{p-1-\gamma}>0$, both regions are bounded by the
order $C(R)\varepsilon_k^{-\gamma}$ (the exponent identity $\delta/\beta=\gamma$,
$\delta=\beta(p-1)-sp$), which diverges as $\varepsilon_k\to0$.
\end{proof}

\begin{remark}\label{rem:tail-upper}
The estimate of Proposition~\ref{prop:tailobstruction}(2) is an
\emph{upper}-bound obstruction: the best available bounds permit tail growth of
order $\varepsilon_k^{-\gamma}$, which is why standard H\"older compactness
cannot be obtained from local $L^\infty$-bounds. We do \emph{not} assert a
matching lower bound $\Tail(v_k)\gtrsim\varepsilon_k^{-\gamma}$; that would
require a saturation (lower-mass-on-annuli) hypothesis on the $v_k$, which we
do not impose.
\end{remark}

\subsection{Truncation: oscillation control, but not constant control}
A natural attempt to bypass the tail obstruction is to truncate $v_k$ at an
intermediate scale and carry the far field as a datum. This controls the
\emph{oscillation} of the resulting error but not its (possibly divergent)
constant part. Fix $\eta\in C^1_c(\R^n)$ with $0\le\eta\le1$, $\eta\equiv1$ on
$B_1$, $\eta\equiv0$ off $B_2$. For $R_k\to\infty$ set $\eta_k(y)=\eta(y/R_k)$
and $\tilde v_k:=\eta_k v_k$. For a fixed ball $B_R$ with $R\ll R_k$ one has
$\tilde v_k=v_k$ on $B_{R_k}$, so for $x\in B_R$ the singular part cancels and
\[
  E_k(x):=\fpl{\tilde v_k}(x)-\fpl{v_k}(x)
  =\int_{|y|>R_k}\frac{J_p(v_k(x)-\eta_k(y)v_k(y))-J_p(v_k(x)-v_k(y))}
   {|x-y|^{n+sp}}\,dy,
\]
absolutely convergent since $\tilde v_k$ is compactly supported.

\begin{lemma}[Truncation oscillation estimate]\label{lem:trunc}
Assume, for large $k$, $\sup_{B_R}|v_k|\le A$, $\sup_{B_R}|\nabla v_k|\le L_R$,
$|v_k(y)|\le A(1+|y|)^{\beta}$ for $|y|\le 2R_k$, and $|v_k(y)|\le B_k$ on
$\R^n$. Write $E_k=a_k+g_k$ with $a_k:=E_k(0)$, $g_k:=E_k-E_k(0)$. Then
\[
  \|\nabla g_k\|_{L^\infty(B_R)}\le C\Big[
   R_k^{\beta(p-2)-sp}+R_k^{\beta(p-1)-sp-1}
   +B_k^{p-2}R_k^{-sp}+B_k^{p-1}R_k^{-sp-1}\Big],
\]
$C=C(n,s,p,\eta,R,A,L_R)$. In the blow-up case $R_k\sim c/r_k$,
$B_k=M/(\theta_k r_k^{\beta})$, this yields $\|\nabla g_k\|_{L^\infty(B_R)}\to0$
provided
\[
  \beta(p-1)<sp+1
  \qquad\Big(\Longleftrightarrow\ \gamma<\tfrac{p-1}{1+sp}\Big),
\]
which, since $\beta>1$, also forces $\beta(p-2)<sp$.
\end{lemma}
\begin{proof}
With $N_k(x,y)=J_p(v_k(x)-\eta_k(y)v_k(y))-J_p(v_k(x)-v_k(y))$ one has
$E_k(x)=\int_{|y|>R_k}N_k(x,y)|x-y|^{-n-sp}dy$, and for $x\in B_R$,
$|y|>R_k\gg R$, $|x-y|\sim|y|$. Two contributions to $\nabla_x E_k$. (i)
\emph{Numerator}: since $J_p\in C^1$ with $|J_p'(t)|=(p-1)|t|^{p-2}$,
$|\nabla_xN_k(x,y)|\le C|\nabla v_k(x)|(1+|v_k(y)|)^{p-2}\le
CL_R(1+|v_k(y)|)^{p-2}$; splitting $\{R_k<|y|<2R_k\}$ (where $|v_k|\le A|y|^\beta$)
from $\{|y|>2R_k\}$ (where $|v_k|\le B_k$) gives the first and third terms. (ii)
\emph{Denominator}: $|\nabla_x|x-y|^{-n-sp}|\le C|y|^{-n-sp-1}$ and
$|N_k(x,y)|\le C(1+|v_k(y)|)^{p-1}$; the same splitting gives the second and
fourth terms. Substituting $R_k\sim c/r_k$, $B_k=M/(\theta_k r_k^\beta)$ and
using $\beta(p-1-\gamma)=sp$ gives the four terms
$r_k^{sp-\beta(p-2)},\,r_k^{sp+1-\beta(p-1)},\,
\theta_k^{-(p-2)}r_k^{sp-\beta(p-2)},\,\theta_k^{-(p-1)}r_k^{sp+1-\beta(p-1)}$,
all $\to0$ under $\beta(p-1)<sp+1$.
\end{proof}

\begin{remark}[Truncation controls oscillation, not the constant]\label{rem:trunc}
Under $\beta(p-1)<sp+1$, Lemma~\ref{lem:trunc} gives $E_k=a_k+o_{C^1(B_R)}(1)$:
truncation converts the far field into a \emph{nearly constant} forcing term.
It does \emph{not} bound $a_k$. Indeed
$|a_k|=|E_k(0)|\lesssim\int_{|y|>R_k}(1+|v_k(y)|)^{p-1}|y|^{-n-sp}dy\sim
R_k^{\beta(p-1)-sp}=r_k^{-\delta}$, with $\delta:=\beta(p-1)-sp>0$, which
\emph{diverges}; the $x$-oscillation gains exactly one power $|y|^{-1}\sim r_k$,
turning $r_k^{-\delta}$ into $r_k^{1-\delta}\to0$ (valid precisely when
$\delta<1$, i.e.\ $\beta(p-1)<sp+1$), but leaves the constant uncontrolled. For
$p=2$ the constant is removed by passing to (second) differences; for $p\neq2$
it cannot be removed from the nonlinear equation for $v_k$ itself, and no a
posteriori bound on $a_k$ follows from these hypotheses. Hence
\[
  \textbf{truncation alone does not close compactness for }v_k;
  \textbf{ it must be combined with differencing.}
\]
The hypothesis $\sup_{B_R}|\nabla v_k|\le L_R$ is itself part of the conditional
$C^1$ input (Remark~\ref{rem:baseline}).
\end{remark}

\subsection{Truncation combined with differencing}\label{ssec:truncdiff}
The divergent constant $a_k$ of Remark~\ref{rem:trunc} can be removed by passing
to increments before truncating, \emph{provided} the constant either cancels
(as at $p=2$) or is controlled by a far-field increment estimate of the data.
We carry out the construction; the outcome is that the constant cancels for
$p=2$ but not for $p\neq2$, where its control is a genuinely new input.

Let $w_k^h:=v_k(\cdot+h)-v_k$. By Proposition~\ref{prop:linincr} and the
equation for $v_k$,
\begin{equation}\label{eq:incr-eq-vk}
  L_{k,h}w_k^h=f_k^h\quad\text{in }B_{1/r_k},\qquad
  f_k^h:=\theta_k^{\gamma-(p-1)}\big[\Phi(v_k)(\cdot+h)-\Phi(v_k)\big]\to0,
\end{equation}
where $\Phi(t)=t_+^\gamma-t_-^\gamma$ and $L_{k,h}=L_{K_{k,h}}$ has the
increment kernel $K_{k,h}=(p-1)\int_0^1|(1-t)(v_k(x)-v_k(y))+t(v_k(x+h)-v_k(y+h))|^{p-2}dt$.
Truncate $\tilde w_k^h:=\eta(\cdot/R_k)w_k^h$, $R_k\sim c/r_k$; for $x\in B_R$,
\begin{equation}\label{eq:trunc-incr}
  L_{k,h}\tilde w_k^h=f_k^h+a_k(h)+g_k^h,\qquad
  a_k(h):=F_k^h(0),\quad g_k^h:=F_k^h-F_k^h(0),
\end{equation}
where $F_k^h(x)=\int(1-\eta(y/R_k))w_k^h(y)\,K_{k,h}(x,y)|x-y|^{-n-sp}\,dy$.

\begin{lemma}[Increment truncation: oscillation control]\label{lem:trunc-incr}
Assume the local bounds $|v_k|+|\nabla v_k|\le C_R$ on $B_{R+|h|}$, the
far-field growth $|v_k(y)|\le C(1+|y|)^{\beta}$, hence
$|w_k^h(y)|\le C_h(1+|y|)^{\beta-1}$, and \textnormal{(}for the kernel-gradient
bound\textnormal{)} either $p\ge3$ or a uniform non-cancellation lower bound on
$K_{k,h}$. Then, for $x\in B_R$,
\[
  \|\nabla g_k^h\|_{L^\infty(B_R)}\le C_h\big(
   R_k^{\beta(p-2)-sp-1}+R_k^{\beta(p-1)-sp-2}\big)\ \longrightarrow\ 0
\]
under $\beta(p-1)<sp+1$ \textnormal{(}$\Leftrightarrow\gamma<\frac{p-1}{1+sp}$\textnormal{)}.
This decay is \emph{one power better} than the direct truncation
\textnormal{(}Lemma~\ref{lem:trunc}\textnormal{)}, since $w_k^h$ grows like
$|y|^{\beta-1}$ rather than $|y|^{\beta}$.
\end{lemma}
\begin{proof}
Near the far field $|x-y|\sim|y|$, $|K_{k,h}(x,y)|\le C_R(1+|y|)^{\beta(p-2)}$
and $|\nabla_xK_{k,h}(x,y)|\le C_R(1+|y|)^{\beta(p-3)}$ (the latter under the
$p\ge3$/non-cancellation hypothesis). Splitting $\nabla_xF_k^h$ into the
kernel-gradient term $I_1\lesssim\int_{R_k}^\infty\rho^{\beta-1+\beta(p-3)-sp-1}d\rho
=R_k^{\beta(p-2)-sp-1}$ and the denominator-gradient term
$I_2\lesssim\int_{R_k}^\infty\rho^{\beta-1+\beta(p-2)-sp-2}d\rho
=R_k^{\beta(p-1)-sp-2}$ gives the bound; both exponents are negative under
$\beta(p-1)<sp+1$.
\end{proof}

The \emph{constant} $a_k(h)$, however, behaves like the direct case. If the
increment growth $|w_k^h(y)|\le C_h(1+|y|)^{\beta-1}$ held \emph{globally} then
$|a_k(h)|\lesssim R_k^{\beta(p-1)-sp-1}=r_k^{1-\delta}\to0$
($\delta=\beta(p-1)-sp<1$). But for actual blow-ups only the global $L^\infty$
bound $|w_k^h|\le 2M/\varepsilon_k$ is available beyond $\sim1/r_k$, giving an
outer contribution $\sim M^{p-1}\theta_k^{-(p-1)}r_k^{\,sp-\beta(p-1)}
=M^{p-1}\theta_k^{-(p-1)}r_k^{-\delta}$, which need \emph{not} vanish.

\begin{proposition}[$p=2$: the constant cancels]\label{prop:p2cancel}
For $p=2$, $K_{k,h}\equiv c_{n,s}$ and $L_{k,h}=(-\Delta)^s$ is linear and
translation invariant, so $(-\Delta)^s\Delta_\ell=\Delta_\ell(-\Delta)^s$.
Applying a further difference to \eqref{eq:trunc-incr} gives
$(-\Delta)^s\Delta_\ell\tilde w_k^h=\Delta_\ell f_k^h+\Delta_\ell g_k^h$,
in which the constant $a_k(h)$ has cancelled ($\Delta_\ell a_k(h)=0$). Hence
truncation $+$ second differencing closes the constant-mode problem at $p=2$
\textnormal{(}the PTU mechanism\textnormal{)}.
\end{proposition}

\begin{proposition}[$p\neq2$: the constant is not removed]\label{prop:pneq2}
For $p\neq2$ the cancellation of Proposition~\ref{prop:p2cancel} fails, for
three independent reasons.
\begin{enumerate}[leftmargin=2em]
\item \emph{No commutator identity.} Since $K_{k,h}$ depends on $v_k$,
$L_{k,h}\Delta_\ell\neq\Delta_\ell L_{k,h}$; the commutator
$\Delta_\ell(L_{k,h}\tilde w_k^h)-L_{k,h}\Delta_\ell\tilde w_k^h$ contains the
$x$-oscillation $K_{k,h}(x+\ell,y)|x+\ell-y|^{-n-sp}-K_{k,h}(x,y)|x-y|^{-n-sp}$,
which depends on $Dv_k$ and degenerates where $Dv_k=0$; it is not small under
the present hypotheses.
\item \emph{No exact cocycle for $a_k$.} While $w^{h+\ell}=w^h(\cdot+\ell)+w^\ell$,
the constants $a_k(h+\ell),a_k(h),a_k(\ell)$ carry the distinct kernels
$K_{k,h+\ell},K_{k,h},K_{k,\ell}$; the defect $a_k(h+\ell)-a_k(h)-a_k(\ell)$ is
a sum of kernel-difference integrals, small only under the same global
increment control that fails for blow-ups.
\item \emph{No a posteriori bound from local regularity.} Pointwise evaluation
of $L_{k,h}\tilde w_k^h(0)$ requires regularity above the operator order
$sp-p+2$, whereas \cite[\S7]{GJS} supplies only a H\"older estimate; and weak
testing $a_k(h)\int\varphi=\mathcal E_{K_{k,h}}(\tilde w_k^h,\varphi)-\int(f_k^h+g_k^h)\varphi$
needs a \emph{uniform energy bound} for $\tilde w_k^h$ in $K_{k,h}$, which is
itself another compactness/tail input. Hence no bound on $a_k(h)$ follows.
\end{enumerate}
\end{proposition}

\begin{lemma}[Conditional compactness for increments]\label{lem:truncdiff}
Assume $p\ge2$, $s>1-\frac1p$, $p<\frac2{1-s}$, $\beta(p-1)<sp+1$; the kernels
$K_{k,h}$ satisfy the GJS-type hypotheses on $B_{2R}$ \textnormal{(}symmetry,
scaled upper bound, coercivity of order $sp-p+2$\textnormal{)} with constants
independent of $k$; the local bounds of Lemma~\ref{lem:trunc-incr}; and the
\emph{constant-mode control}
\[
  \textnormal{(CM)}\qquad |a_k(h)|\le C_h\quad\text{(better: }a_k(h)\to0\text{)}.
\]
Then $\tilde w_k^h\to w_0^h$ in $C^{\asp}_{loc}$ along a subsequence, and the
limit increment solves $L_{K_0}w_0^h=c(h)$ with $c(h)=\lim a_k(h)$. If
$a_k(h)\to0$ the limit equation is homogeneous; if $a_k(h)\to a(h)\neq0$ it is
inhomogeneous with a constant right-hand side, which does \emph{not} suffice for
the Liouville step unless the constant can be removed.
\end{lemma}

\begin{remark}[The precise missing input]\label{rem:farfield}
By Propositions~\ref{prop:p2cancel}--\ref{prop:pneq2}, for $p\neq2$ the
constant-mode hypothesis \textnormal{(CM)} is \emph{not} a consequence of local
regularity, the cocycle, or differencing. It is equivalent to a
\emph{uniform far-field increment estimate of the data},
\[
  |v_k(y+h)-v_k(y)|\ \lesssim_h\ (1+|y|)^{\beta-1}\quad\text{globally in }y,
\]
i.e.\ $a_k(h)\to0$ --- which is precisely the information that local behavior
near the free boundary does not supply. This, not the size of the truncation
oscillation, is the exact remaining obstruction to compactness for $p\neq2$;
\[
  \textbf{truncation }+\textbf{ differencing closes }p=2\textbf{, but for }
  p\neq2\textbf{ it requires uniform far-field increment control.}
\]
\end{remark}

\begin{remark}[The constant as a degree-zero polynomial: the DSV viewpoint]\label{rem:dsv}
The constant $a_k(h)$ is a degree-$0$ polynomial. In the polynomial-growth
framework of Dipierro--Savin--Valdinoci~\cite{DSV}, where the equation is read
\emph{modulo polynomials}, such a constant is identified with $0$, so the
far-field constant is not part of the meaningful limit equation. At $p=2$ this
is exactly the second-difference mechanism (Proposition~\ref{prop:p2cancel}),
and \cite{DSV} makes it rigorous. For $p\neq2$ the same viewpoint indicates the
correct formulation --- $L_{K_h}w^h=0$ \emph{modulo constants} --- but
\cite{DSV}, and the measurable-kernel Schauder theory of~\cite{FRO,Serra}, are
established for \emph{uniformly elliptic} kernels, not for the variable,
degenerate kernel $K_h$. The needed modulo-polynomial stability/Liouville
theory for $L_{K_h}$ is therefore a genuine new input, not a citation
(Section~\ref{sec:open}). \emph{This reframes the obstruction: the constant is
not mysterious, it is a degree-zero polynomial obstruction; handled by the
\textnormal{DSV/PTU} framework at $p=2$, and requiring its degenerate-kernel
analogue for $p\neq2$.}
\end{remark}

Independently of the modulo-polynomial route, the constant can be made to
vanish under a regularity hypothesis on the \emph{exterior data} alone.

\begin{lemma}[Stability under exterior H\"older data]\label{lem:exterior}
Suppose the exterior data are uniformly H\"older,
$|u_k(x)-u_k(y)|\le C|x-y|^{\sigma}$ for $x,y\in\R^n\setminus B_1$, with
\[
  \sigma>\delta:=\beta(p-1)-sp\ \ (>0).
\]
Then the far-field constant of \eqref{eq:trunc-incr} satisfies
$|a_k(h)|\lesssim|h|^{\sigma}\,\theta_k^{-(p-1)}\,r_k^{\,\sigma-\delta}\to0$. In
particular, since $\delta<1$ under the tail condition~\eqref{eq:tailcond},
\emph{exterior Lipschitz data $(\sigma=1)$ suffices}, and the constant-mode
hypothesis \textnormal{(CM)} of Lemma~\ref{lem:truncdiff} holds.
\end{lemma}
\begin{proof}
For $|y|>R_k\sim 1/r_k$ one has $r_ky\notin B_1$, so the exterior modulus gives
$|w_k^h(y)|=\theta_k^{-1}r_k^{-\beta}|u_k(r_ky+r_kh)-u_k(r_ky)|\le
C|h|^{\sigma}\theta_k^{-1}r_k^{\sigma-\beta}$. With
$|K_{k,h}(0,y)|\lesssim|v_k(y)|^{p-2}\le(M\theta_k^{-1}r_k^{-\beta})^{p-2}$ and
$\int_{|y|>R_k}|y|^{-n-sp}dy\sim r_k^{sp}$,
\[
  |a_k(h)|\lesssim |h|^{\sigma}\,\theta_k^{-1}r_k^{\sigma-\beta}\cdot
   \theta_k^{-(p-2)}r_k^{-\beta(p-2)}\cdot r_k^{sp}
   =|h|^{\sigma}\,\theta_k^{-(p-1)}\,r_k^{\,\sigma-\delta}.\qedhere
\]
\end{proof}

\begin{remark}\label{rem:exterior}
Lemma~\ref{lem:exterior} turns the stability obstruction into a
\emph{checkable hypothesis on the data}: any solution whose exterior values are
Lipschitz (e.g.\ $u$ globally Lipschitz, or the exterior datum chosen smooth)
satisfies \textnormal{(CM)}, so for such solutions compactness \emph{and}
stability are in place, and the only remaining input of
Theorem~\ref{thm:growth} is the Liouville step.
\end{remark}

\begin{remark}\label{rem:nocompact}
Known interior H\"older estimates for fractional $p$-Laplacian equations
contain tail terms. Therefore \emph{local $L^\infty$-bounds alone are not
enough to obtain compactness of $(v_k)$}: by
Proposition~\ref{prop:tailobstruction} the tail term entering such estimates
diverges, so the sequence is not, a priori, precompact even in
$C^0_{loc}$. Any compactness statement must either supply uniform tail control
or replace $v_k$ by a modified (truncated or differenced) sequence; we do
\emph{not} assume compactness silently. This is the content of
Assumption~\ref{ass:compact}.
\end{remark}

%======================================================================
\section{Affine subtraction and shifted kernels: perturbative compactness}
\label{sec:shifted}
%======================================================================
For $p=2$, subtracting an affine function from a solution produces a solution;
for $p\neq2$ it does not. The correct mechanism is to move the affine part
\emph{into the operator}. For $b\in\R^n$ define, formally,
\begin{equation}\label{eq:Ab}
  A_b v(x):=\mathrm{P.V.}\!\int_{\R^n}
   J_p\big(v(x)-v(y)+b\cdot(x-y)\big)\,\frac{dy}{|x-y|^{n+sp}},
  \qquad J_p(t)=\Jp{t},
\end{equation}
so that if $\fpl{v}=f$ and $\ell(x)=a+b\cdot x$, then $w=v-\ell$ satisfies
$A_bw=f$. The operator $A_b$ is \emph{monotone}, since for fixed $\tau\in\R$,
\begin{equation}\label{eq:mono}
  \big(J_p(\xi+\tau)-J_p(\eta+\tau)\big)(\xi-\eta)\ \ge\ 0,
\end{equation}
$J_p$ being nondecreasing. This section proves the compactness/limit-equation
half of the perturbative scheme for the family $\{A_b\}_{|b|\le B}$. The key
structural point, which simplifies everything, is a \emph{conjugation
identity}: on the class of functions whose far field carries the affine
structure as data, $A_b$ is the ordinary operator in disguise, and no
exotic formulation is needed.

\subsection{Two exterior classes, and the conjugation identity}
The expression \eqref{eq:Ab} requires care in the far field. Exactly what
care depends on the structure of the exterior data, and we distinguish two
classes; conflating them produces incorrect estimates.

\begin{definition}[Admissible classes]\label{def:classes}
Let $b\in\R^n$, $v\in W^{s,p}(B_2)\cap L^\infty(B_2)$.
\begin{itemize}[leftmargin=2em]
\item[\textnormal{(A)}] \emph{Affine-structured exterior:} $v=g-\ell_b$ on
$\R^n\setminus B_2$, where $\ell_b(x)=b\cdot x$ and $g\in L^{p-1}_{sp}(\R^n)$,
i.e.\ $\Tail(g;0,2)<\infty$.
\item[\textnormal{(B)}] \emph{Bounded exterior:} $v\in L^\infty(\R^n)$
\textnormal{(}no affine structure at infinity\textnormal{)}.
\end{itemize}
\end{definition}

\begin{lemma}[Conjugation; class \textnormal{(A)} needs no compensation]
\label{lem:conj}
Let $v$ be of class \textnormal{(A)} and set $V:=v+\ell_b$. Then $V\in
W^{s,p}(B_2)\cap L^\infty(B_2)$, $V=g$ on $\R^n\setminus B_2$, so
$V\in L^{p-1}_{sp}(\R^n)$, and for every $\varphi\in C_c^\infty(B_1)$ the
\emph{ordinary} weak form
\[
  \mathcal E(V,\varphi):=\frac12\iint_{\R^n\times\R^n}
   J_p\big(V(x)-V(y)\big)\,\frac{(\varphi(x)-\varphi(y))}{|x-y|^{n+sp}}
   \,dx\,dy
\]
converges absolutely, under the \emph{standard} tail assumption on $g$ only
--- no restriction beyond $p>sp$ \textnormal{(}always true\textnormal{)} is
needed. We \emph{define} $A_bv=f$ weakly in $B_1$ to mean
$\mathcal E(V,\varphi)=\int f\varphi$ for all such $\varphi$; formally
$A_bv=\fpl{V}$, i.e.\ the shift is conjugated away.
\end{lemma}
\begin{proof}
Near region ($x,y\in B_2$): the standard estimate, using
$V\in W^{s,p}(B_2)\cap L^\infty(B_2)$ (the affine part is bounded on $B_2$).
Far cross region ($x\in\operatorname{supp}\varphi\subset B_1$,
$y\notin B_2$): here $V(y)=g(y)$ and
$|J_p(V(x)-g(y))|\le c\,\big(\|V\|_{L^\infty(B_2)}^{p-1}+|g(y)|^{p-1}\big)$,
so
\[
  \int_{B_1}|\varphi(x)|\int_{\R^n\setminus B_2}
  \frac{|J_p(V(x)-g(y))|}{|x-y|^{n+sp}}\,dy\,dx
  \ \le\ C\Big(\|V\|_{L^\infty(B_2)}^{p-1}+\Tail(g;0,2)^{p-1}\Big)
  \|\varphi\|_{L^1},
\]
using $|x-y|\ge\frac13(1+|y|)$ for $x\in B_1$, $y\notin B_2$. Absolute
convergence holds with no exponent restriction.
\end{proof}

\begin{remark}[Correction of a previous formulation]\label{rem:correction}
An earlier version of this section introduced a ``compensated'' far-field
pairing, subtracting $J_p(b\cdot(x-y))$, and estimated the remainder by
$|J_p(\tau+\xi)-J_p(\tau)|\le C_p(|\tau|+|\xi|)^{p-2}|\xi|$ with
$\tau=b\cdot(x-y)$. For class \textnormal{(A)} this is both unnecessary
\textnormal{(}Lemma~\ref{lem:conj}\textnormal{)} and, as written, flawed: the
increment $\xi=v(x)-g(y)+b\cdot y$ is \emph{unbounded}, so the split does not
close. The compensated formulation is meaningful precisely for class
\textnormal{(B)}, where it is also sharp; see Lemma~\ref{lem:classB}.
\end{remark}

\begin{lemma}[Class \textnormal{(B)}: compensated formulation and its exact
cost]\label{lem:classB}
Let $v$ be of class \textnormal{(B)}. Define
\begin{align*}
  \mathcal E_b^{\mathrm{comp}}(v,\varphi):={}&\frac12\iint_{\{|x-y|\le1\}}
    J_p\big(v(x)-v(y)+b\cdot(x-y)\big)\,
    \frac{(\varphi(x)-\varphi(y))}{|x-y|^{n+sp}}\,dx\,dy\\
  &+\int\varphi(x)\!\int_{\{|x-y|>1\}}
    \Big[J_p\big(v(x)-v(y)+b\cdot(x-y)\big)-J_p\big(b\cdot(x-y)\big)\Big]
    \frac{dy\,dx}{|x-y|^{n+sp}},
\end{align*}
with the convention
$\int_{\{|x-y|>1\}}J_p(b\cdot(x-y))|x-y|^{-n-sp}dy=0$
\textnormal{(}odd symmetry; exact on every annulus $\{1<|x-y|<R\}$, hence in
the improper limit\textnormal{)}. Then:
\begin{itemize}[leftmargin=2em]
\item[\textnormal{(i)}] If $v\in L^\infty(\R^n)$, the far-field integrand
obeys, with $\tau=b\cdot(x-y)$ and the \emph{bounded} increment
$\xi=v(x)-v(y)$,
\[
  \big|J_p(\tau+\xi)-J_p(\tau)\big|
  \le C_p\big(|\tau|+|\xi|\big)^{p-2}|\xi|
  \le C_p\big(B|x-y|+2\|v\|_\infty\big)^{p-2}\,2\|v\|_\infty
  \ \lesssim\ |x-y|^{p-2},
\]
and $\int_{|x-y|>1}|x-y|^{p-2-n-sp}\,dy<\infty$ \emph{iff} $p-2<sp$. Thus for
bounded exterior data the compensated formulation is well posed exactly in
the range $p<\frac2{1-s}$, and this restriction is genuinely a far-field
requirement here, not only a near-field one.
\item[\textnormal{(ii)}] If $v$ is unbounded with only the standard tail
$\int_{|y|>1}|v(y)|^{p-1}|y|^{-n-sp}dy<\infty$, the mixed term
$|\tau|^{p-2}|\xi|$ produces the requirement
\begin{equation}\label{eq:mixed-tail}
  \int_{|y|>1}\frac{|x-y|^{\,p-2}\,|v(y)|}{|x-y|^{n+sp}}\,dy
  \ \simeq\
  \int_{|y|>1}\frac{|v(y)|}{|y|^{\,n+sp-(p-2)}}\,dy\ <\ \infty,
\end{equation}
a \emph{mixed tail} that is strictly stronger than the $(p-1)$-tail in
general when $sp\le p-1$ \textnormal{(}H\"older interpolation fails to reduce
one to the other: the conjugate exponent costs
$\int|y|^{p-1-n-sp}=\infty$\textnormal{)}. For $b\neq0$ and unbounded class
\textnormal{(B)} data, \eqref{eq:mixed-tail} must be \emph{assumed}.
\end{itemize}
\end{lemma}
\begin{proof}
(i) is the displayed computation; the annular cancellation of the reference
term is exact by oddness of $z\mapsto J_p(b\cdot z)|z|^{-n-sp}$ on symmetric
annuli. (ii): expand $(|\tau|+|\xi|)^{p-2}\le
c(|\tau|^{p-2}+|\xi|^{p-2})$; the term $|\xi|^{p-2}|\xi|=|\xi|^{p-1}$ is
controlled by the standard $(p-1)$-tail, while $|\tau|^{p-2}|\xi|$ gives
\eqref{eq:mixed-tail}; the stated failure of interpolation is checked on
$v(y)=|y|^{\sigma}$ with $\sigma$ slightly below $\frac{sp}{p-1}$:
the $(p-1)$-tail converges while \eqref{eq:mixed-tail} requires
$\sigma<sp-p+2$, a strictly stronger condition when $sp\le p-1$.
\end{proof}

\begin{remark}[Which class is used where]\label{rem:whichclass}
The blow-up/excess iteration produces functions of class \textnormal{(A)}:
the affine part is a \emph{local normalization}, while the far field is the
(rescaled) original solution, which has a finite standard tail; a direct
computation shows the rescalings preserve class \textnormal{(A)} with
improving tails, since the normalization is subcritical
($(1+\al')(p-1)<sp$). Truncated increments, by contrast, are of class
\textnormal{(B)} with \emph{bounded} data, so Lemma~\ref{lem:classB}(i)
applies to them in the range $p<\frac2{1-s}$; the dangerous case (ii) does
not arise in our scheme. All statements below are formulated for class
\textnormal{(A)} unless stated otherwise.
\end{remark}

\begin{remark}[No pointwise operator is used]\label{rem:no-pointwise}
We never evaluate \eqref{eq:Ab} pointwise: all statements below are in the
weak senses of Lemma~\ref{lem:conj} (class (A)) or Lemma~\ref{lem:classB}
(class (B)). The odd-symmetry convention in Lemma~\ref{lem:classB} is the
nonlinear analogue of the polynomial-compensated definitions available for
$(-\Delta)^s$ \textnormal{(}\cite{DSV}, linear only\textnormal{)}.
\end{remark}

\subsection{Perturbative compactness}

\begin{proposition}[Compactness and the limit equation for shifted
operators]\label{prop:P1}
Let $2\le p<\frac2{1-s}$ and $B\ge0$. Let $b_k\in\R^n$, $|b_k|\le B$,
$b_k\to b$, and let $v_k$ be of class \textnormal{(A)} and satisfy, in the
sense of Lemma~\ref{lem:conj},
\[
  A_{b_k}v_k=f_k\quad\text{weakly in }B_1,
  \qquad \|f_k\|_{L^\infty(B_1)}\to0,
\]
with the uniform bounds
\[
  \|v_k\|_{L^\infty(B_2)}\le C_0,\qquad
  [v_k]_{W^{s,p}(B_2)}\le C_0,\qquad
  \|v_k\|_{C^{0,1}(B_{3/2})}\le C_0,
\]
and far-field decompositions $v_k=g_k-\ell_{b_k}$ on $\R^n\setminus B_2$
satisfying \emph{either}
\begin{itemize}[leftmargin=2em]
\item[\textnormal{(E1)}] shared exterior data: $g_k\equiv g$ with
  $g\in L^{p-1}_{sp}(\R^n)$; \emph{or}
\item[\textnormal{(E2)}] tail convergence: $g_k\to g_0$ a.e.\ on
  $\R^n\setminus B_2$ and in $L^{p-1}_{sp}$, i.e.
  $\int_{\R^n\setminus B_2}\frac{|g_k-g_0|^{p-1}}{1+|y|^{n+sp}}\,dy\to0$,
  with $\sup_k\Tail(g_k;0,2)<\infty$.
\end{itemize}
Then, along a subsequence,
\[
  v_k\to v_0\ \text{locally uniformly in }B_{3/2},
  \qquad
  v_k\rightharpoonup v_0\ \text{weakly in }W^{s,p}_{loc}(B_{3/2}),
\]
and the limit satisfies
\[
  A_bv_0=0\quad\text{weakly in }B_1 .
\]
No $C^1_{loc}$ convergence is used or asserted, and no strong
$W^{s,p}_{loc}$ convergence is claimed.
\end{proposition}

\begin{proof}
\emph{Step 1: compactness.} The uniform Lipschitz bound on $B_{3/2}$ and
Arzel\`a--Ascoli give $v_k\to v_0$ locally uniformly along a subsequence; the
uniform Gagliardo bound gives $v_k\rightharpoonup v_0$ weakly in
$W^{s,p}(B_r)$ for every $r<2$ \textnormal{(}reflexivity; the two limits
agree a.e.\textnormal{)}. Under (E2), define $v_0:=g_0-\ell_b$ outside $B_2$;
under (E1), $v_0:=g-\ell_b$ there. In either case $v_0$ is of class
\textnormal{(A)}, so the weak sense of Lemma~\ref{lem:conj} is available for
it. By conjugation we work throughout with
$\mathcal V_k:=v_k+\ell_{b_k}$ and $\mathcal V_0:=v_0+\ell_b$: these satisfy
$\fpl{\mathcal V_k}=f_k$ weakly in $B_1$ in the \emph{ordinary} sense,
$\mathcal V_k=g_k$ outside $B_2$, and $\mathcal V_k\to\mathcal V_0$ locally
uniformly \textnormal{(}$b_k\to b$\textnormal{)}.

\emph{Step 2: the Minty device.} Fix $\varphi\in C_c^\infty(B_1)$ and $t>0$,
and set $V:=\mathcal V_0+t\varphi$. By the monotonicity of $J_p$ applied
pointwise in $(x,y)$,
\begin{equation}\label{eq:minty}
  \mathcal E(V,\,V-\mathcal V_k)\ \ge\ \mathcal E(\mathcal V_k,\,V-\mathcal V_k)
  \ =\ \int_{B_1} f_k\,(V-\mathcal V_k)\,\zeta\,dx\ \longrightarrow\ 0,
\end{equation}
where the pairing is localized by a cutoff $\zeta$ as usual; the right-hand
side vanishes since $\|f_k\|_\infty\to0$ and $V-\mathcal V_k$ is uniformly
bounded on $B_1$. \textnormal{(}Admissibility of $V-\mathcal V_k$ as a test
function follows by density from the uniform $W^{s,p}(B_2)\cap L^\infty$
bounds; standard approximation, no new estimate.\textnormal{)}

\emph{Step 3: passing to the limit in the left-hand side of
\eqref{eq:minty}.} The first argument $V$ is \emph{fixed}; the functional
$\mathcal E(V,\cdot)$ is \emph{linear} in its second argument. Split the
double integral at $B_2\times B_2$:
\begin{itemize}[leftmargin=2em]
\item \emph{Near region ($x,y\in B_2$).} The density
$G(x,y):=J_p(V(x)-V(y))$ satisfies
$|G|\le C|x-y|^{p-1}$ \textnormal{(}$V$ Lipschitz on $B_2$\textnormal{)},
hence $G\,|x-y|^{-\frac{n+sp}{p'}}\in L^{p'}(B_2\times B_2)$ with
$p'=\frac{p}{p-1}$, since $(p-1)p'=p$ and
$\iint_{B_2\times B_2}|x-y|^{p-n-sp}<\infty$. The second factor
$(V-\mathcal V_k)(x)-(V-\mathcal V_k)(y)$, weighted by
$|x-y|^{-\frac{n+sp}{p}}$, converges \emph{weakly} in
$L^p(B_2\times B_2)$ by Step~1. A fixed--weak pairing passes to the limit.
\item \emph{Far region ($x\in B_1$, $y\notin B_2$, and symmetric).} The
integrand is
$J_p(V(x)-g_k(y))\,(\text{second factor})\,|x-y|^{-n-sp}$, dominated by the
fixed majorant of Lemma~\ref{lem:conj}
\textnormal{(}uniform under (E1)/(E2)\textnormal{)}, and converges pointwise
a.e.\ by Step~1 and (E1)/(E2). Dominated convergence applies. \emph{This is
the only place the exterior hypothesis is used, and it cannot be dispensed
with}: without (E1)/(E2), far-field mass can create a spurious right-hand
side in the limit \textnormal{(}the counterexample of
\cite[Rem.~4.4]{CSapprox} adapts\textnormal{)}.
\end{itemize}
Therefore $\mathcal E(V,V-\mathcal V_k)\to\mathcal E(V,t\varphi)$, and
\eqref{eq:minty} gives $\mathcal E(\mathcal V_0+t\varphi,\varphi)\ge0$ after
dividing by $t>0$.

\emph{Step 4: hemicontinuity.} As $t\downarrow0$,
$J_p(\mathcal V_0(x)-\mathcal V_0(y)+t(\varphi(x)-\varphi(y)))\to
J_p(\mathcal V_0(x)-\mathcal V_0(y))$ pointwise, dominated on the near
region by $C|x-y|^{p-1}$ and on the far region by the majorant of
Lemma~\ref{lem:conj} \textnormal{(}uniformly for $t\le1$\textnormal{)}.
Hence $\mathcal E(\mathcal V_0+t\varphi,\varphi)\to
\mathcal E(\mathcal V_0,\varphi)\ge0$. Replacing $\varphi$ by $-\varphi$
gives $\mathcal E(\mathcal V_0,\varphi)=0$, i.e.\ $A_bv_0=0$ weakly in
$B_1$ in the sense of Lemma~\ref{lem:conj}.
\end{proof}

\begin{remark}[What Proposition~\ref{prop:P1} does and does not use]
The proof uses: local uniform convergence, weak $W^{s,p}_{loc}$ compactness,
monotonicity, and dominated far-field convergence. It does \emph{not} use:
strong $W^{s,p}$ convergence, any $C^1$ information, or any regularity of the
limit beyond Lipschitz. The Lipschitz hypothesis itself is supplied in
applications by the inhomogeneous baseline~\cite{BT}, which holds in the same
range $p<\frac2{1-s}$.
\end{remark}

\subsection{The regularity input: proved for class (A), open for class (B)}

\begin{proposition}[Shifted homogeneous $C^{1,\al}$ estimate, class
\textnormal{(A)}: proved by conjugation]\label{prop:P2A}
Let $2\le p<\frac2{1-s}$, $B>0$, $|b|\le B$. Let $v$ be of class
\textnormal{(A)} with $A_bv=0$ weakly in $B_2$
\textnormal{(}Lemma~\ref{lem:conj}\textnormal{)},
$\|v\|_{L^\infty(B_2)}\le1$ and $\Tail(g;0,2)\le1$. Then there are
$\al_0=\al_0(n,s,p)\in(0,1)$ and $C=C(n,s,p,B)$ with
\[
  \|v\|_{C^{1,\al_0}(B_{1/2})}\ \le\ C .
\]
\end{proposition}
\begin{proof}
Set $\mathcal V:=v+\ell_b$. By Lemma~\ref{lem:conj}, $\mathcal V$ is an
ordinary weak solution of $\fpl{\mathcal V}=0$ in $B_2$, with
$\|\mathcal V\|_{L^\infty(B_2)}\le 1+2B$ and
$\Tail(\mathcal V;0,2)=\Tail(g;0,2)\le1$ \textnormal{(}$\mathcal V=g$
outside $B_2$\textnormal{)}. Thus $\mathcal V$ satisfies \emph{verbatim} the
hypotheses of \cite[Theorem~1.1]{GJS}, whence
$\|\mathcal V\|_{C^{1,\al_0}(B_{1/2})}\le C(n,s,p)(1+2B+1)$. Subtracting the
affine function returns the estimate for $v$.
\end{proof}

\begin{remark}[Why this is not a cheat, and what remains open]
\label{rem:P2status}
The point is that in class \textnormal{(A)} the affine behavior at infinity
is \emph{data} ($g$), not the affine extension itself: the conjugated
function $\mathcal V$ has finite tail, so \cite[Thm~1.1]{GJS} applies
directly --- the earlier concern that ``the affine function has infinite
tail when $sp\le p-1$'' pertains only to a \emph{globally} affine far field,
which the blow-up iteration never produces. What remains genuinely open is
the class \textnormal{(B)} analogue \textnormal{(}bounded exterior, shift
not conjugable away\textnormal{)}:
\begin{quote}
\textbf{Hypothesis P2$'$ (class (B) shifted estimate).} For $|b|\le B$ and
$A_bv=0$ in $B_1$ in the compensated sense of Lemma~\ref{lem:classB}, with
$\|v\|_{L^\infty(\R^n)}\le1$: $\|v\|_{C^{1,\al}(B_{1/2})}\le C_B$.
\end{quote}
This would follow from the methods (not the statement) of \cite{GJS}; it is
recorded as an input where used. A second caveat: in the excess iteration
the \emph{normalized} shifts can grow unless the excess is measured against
converging jets (Campanato-style); with that bookkeeping the shifts stay in
a fixed ball $|b|\le B$, and Proposition~\ref{prop:P2A} applies uniformly.
The iteration itself is still not carried out here.
\end{remark}

\begin{corollary}[Compactness toward regular shifted profiles]\label{cor:P1P2}
In the setting of
Proposition~\ref{prop:P1}, by Proposition~\ref{prop:P2A} the limit $v_0$ satisfies
$\|v_0\|_{C^{1,\al_B}(B_{1/2})}\le C_B$, and consequently, for every
$\varepsilon>0$ there is $k_0$ such that for $k\ge k_0$
\[
  \|v_k-v_0\|_{L^\infty(B_{1/2})}\le\varepsilon,
  \qquad v_0\in C^{1,\al_B}(B_{1/2}),\ A_bv_0=0 .
\]
That is: sequences with vanishing right-hand sides are compact, in
$L^\infty(B_{1/2})$, toward shifted homogeneous profiles enjoying full
$C^{1,\al}$ regularity. \textnormal{(}The closeness is in $L^\infty$, not
$C^1$: a $C^1$-closeness claim would presuppose gradient equicontinuity of
$v_k$, which is not available at this stage.\textnormal{)}
\end{corollary}

\subsection{Perturbative excess improvement: the Campanato iteration}
\label{ssec:excess}
We now assemble Propositions~\ref{prop:P1} and~\ref{prop:P2A} into an excess
iteration. By the conjugation of Lemma~\ref{lem:conj} it suffices to treat
the \emph{ordinary} equation: throughout this subsection
\[
  \fpl{V}=f\ \text{ weakly in }B_1,\qquad
  \|V\|_{L^\infty(B_1)}\le1,\qquad \Tail(V;0,1)\le1 ,
\]
and the shifted case $A_bv=f$ is recovered by setting $V=v+\ell_b$. The
shifts then reappear \emph{inside} the iteration, through the normalized
frames; their bookkeeping is the delicate point and is treated explicitly.

\subsubsection*{Step 1: one-step approximation}
\begin{lemma}[Approximation by shifted-harmonic profiles]\label{lem:E1}
Let $2\le p<\frac2{1-s}$ and $B\ge0$. For every $\eta>0$ there exists
$\varepsilon_0=\varepsilon_0(n,s,p,B,\eta)>0$ such that: if $|b|\le B$, $v$
is of class \textnormal{(A)} with $\|v\|_{L^\infty(B_1)}\le1$, normalized
tails, and $A_bv=f$ in $B_1$ with $\|f\|_{L^\infty(B_1)}\le\varepsilon_0$,
then there exists $w$ with
\[
  A_bw=0\ \text{ in }B_{3/4},
  \qquad
  \|v-w\|_{L^\infty(B_{1/2})}\le\eta .
\]
Only $L^\infty$-closeness is asserted.
\end{lemma}
\begin{proof}
Suppose not: there are $\eta>0$ and sequences $b_k\to b$
\textnormal{(}$|b_k|\le B$; compactness of the ball\textnormal{)}, $v_k$
admissible, $f_k$ with $\|f_k\|_\infty\to0$, such that
\begin{equation}\label{eq:E1-contra}
  \|v_k-w\|_{L^\infty(B_{1/2})}>\eta
  \qquad\text{for \emph{every} $w$ solving }A_{b}w=0\text{ in }B_{3/4}.
\end{equation}
The uniform Lipschitz bound required by Proposition~\ref{prop:P1} holds by
the inhomogeneous baseline~\cite{BT} applied to the conjugated functions
$\mathcal V_k=v_k+\ell_{b_k}$ \textnormal{(}uniformly bounded data on
$B_1$, uniform tails\textnormal{)}. Proposition~\ref{prop:P1} yields, along
a subsequence, $v_k\to v_0$ locally uniformly with $A_bv_0=0$ in
$B_{3/4}$. Taking $w=v_0$ in \eqref{eq:E1-contra} and $k$ large contradicts
the local uniform convergence on $\overline{B_{1/2}}$.
\end{proof}

\subsubsection*{Step 2: one-step affine improvement}
\begin{lemma}[One-step excess decay]\label{lem:E2}
Let $2\le p<\frac2{1-s}$, $B\ge0$, and fix
\begin{equation}\label{eq:alpha-choice}
  0<\al'<\al_0,
  \qquad
  1+\al'<\frac{sp}{p-1},
\end{equation}
with $\al_0$ from Proposition~\ref{prop:P2A}. There exist
$\rho\in(0,\tfrac12)$, $\varepsilon_0>0$ and $C_1=C_1(n,s,p,B)$ such that:
under the hypotheses of Lemma~\ref{lem:E1} with
$\|f\|_{L^\infty(B_1)}\le\varepsilon_0$, there is an affine function
$\ell(x)=a+q\cdot x$ with $|a|+|q|\le C_1$ and
\[
  \sup_{B_\rho}|v-\ell|\ \le\ \rho^{1+\al'} .
\]
\end{lemma}
\begin{proof}
Let $w$ be the approximation of Lemma~\ref{lem:E1} with $\eta$ to be
chosen. By Proposition~\ref{prop:P2A} \textnormal{(}conjugation $+$
\cite[Thm~1.1]{GJS}\textnormal{)},
$\|w\|_{C^{1,\al_0}(B_{1/2})}\le C_1$, so with
$\ell(x):=w(0)+\nabla w(0)\cdot x$,
\[
  \sup_{B_\rho}|w-\ell|\ \le\ C_1\rho^{1+\al_0}
  \qquad(0<\rho<\tfrac12).
\]
Then $\sup_{B_\rho}|v-\ell|\le\eta+C_1\rho^{1+\al_0}$. Choose first
$\rho$ so small that $C_1\rho^{1+\al_0}\le\frac12\rho^{1+\al'}$
\textnormal{(}possible since $\al'<\al_0$\textnormal{)}, then
$\eta:=\frac12\rho^{1+\al'}$, and let $\varepsilon_0$ be the corresponding
threshold from Lemma~\ref{lem:E1}.
\end{proof}

\subsubsection*{Step 3: rescaling and shift bookkeeping}
Suppose inductively that affine functions $L_j(x)=c_j+P_j\cdot x$ satisfy
\begin{equation}\label{eq:excess-j}
  \sup_{B_{\rho^j}}|V-L_j|\ \le\ \rho^{\,j(1+\al')} .
\end{equation}
Define the normalized error
\[
  V_j(x):=\frac{(V-L_j)(\rho^jx)}{\rho^{\,j(1+\al')}} ,
  \qquad \|V_j\|_{L^\infty(B_1)}\le1 .
\]
Writing $\widetilde V_j:=V(\rho^j\cdot)/\rho^{j(1+\al')}$, the scaling
identity of Proposition~\ref{prop:scaling} \textnormal{(}with exponent
$\kappa=1+\al'$\textnormal{)} gives
\begin{equation}\label{eq:fj}
  \fpl{\widetilde V_j}(x)
  =\rho^{\,j\,[sp-(1+\al')(p-1)]}\,f(\rho^jx)=:f_j(x),
  \qquad
  \|f_j\|_\infty\le\rho^{\,j\,[sp-(1+\al')(p-1)]}\,\|f\|_\infty ,
\end{equation}
and the exponent is \emph{positive} precisely by the subcriticality choice
\eqref{eq:alpha-choice}: the right-hand side \emph{improves} along the
iteration. Since
$V_j(x)+\rho^{-j\al'}P_j\cdot x=\widetilde V_j(x)-c_j\rho^{-j(1+\al')}$
and constants are invisible to $J_p$-differences, $V_j$ is of class
\textnormal{(A)} with shift
\begin{equation}\label{eq:bj}
  \boxed{\;b_j=\rho^{-j\al'}\,P_j\;}
\end{equation}
\textnormal{(}plus sign, with the convention that $L_j$ is
\emph{subtracted}\textnormal{)}, and $A_{b_j}V_j=f_j$ in $B_1$. The
exterior data of $V_j$ is the rescaled $V$-datum: on $|y|\le\rho^{-j}$ the
telescoped excess bounds \eqref{eq:excess-j} across intermediate scales
give $|V_j(y)|\le C(1+|y|)^{1+\al'}$, and beyond $\rho^{-j}$ the original
tail of $V$ enters with the improving factor
$\rho^{j[sp-(1+\al')(p-1)]}$; the affine part of $L_j$ is carried in the
class-\textnormal{(A)} structure and is never integrated. Hence $V_j$
satisfies the hypotheses of Lemma~\ref{lem:E2} \emph{provided}
$|b_j|\le B$.

\subsubsection*{Step 4: boundedness of the shifts}
This is \emph{not} automatic. From consecutive excess bounds,
$\sup_{B_{\rho^{j+1}}}|L_{j+1}-L_j|\le2\rho^{j(1+\al')}$, whence
\begin{equation}\label{eq:slope-tel}
  |P_{j+1}-P_j|\ \le\ C\rho^{\,j\al'} ,
\end{equation}
so $P_j\to P_\infty$; but \eqref{eq:bj} shows $|b_j|\to\infty$ whenever
$P_\infty\neq0$. The iteration therefore closes exactly on the set where
the limit slope vanishes, and quantitatively so:

\begin{lemma}[Flatness controls the shifts]\label{lem:E3}
Assume, in addition to \eqref{eq:excess-j} for $j=0$, the flatness
hypothesis
\begin{equation}\label{eq:flat}
  \textnormal{(F)}\qquad
  \sup_{B_r}|V-V(0)|\ \le\ K\,r^{1+\al'}\qquad(0<r\le1).
\end{equation}
Then any affine approximations realizing \eqref{eq:excess-j} satisfy
$|P_j|\le(2K+C)\rho^{j\al'}$, hence
\[
  |b_j|\ \le\ B_*:=2K+C\qquad\text{for all }j .
\]
\end{lemma}
\begin{proof}
Comparing \eqref{eq:excess-j} with \eqref{eq:flat} on $B_{\rho^j}$:
$|P_j\cdot x|\le|V(x)-V(0)|+|V(x)-L_j(x)|+|c_j-V(0)|
\le K\rho^{j(1+\al')}+2\rho^{j(1+\al')}+|c_j-V(0)|$ for $|x|\le\rho^j$, and
$|c_j-V(0)|\le K\rho^{j(1+\al')}+\rho^{j(1+\al')}$ by evaluating at $x=0$.
Taking the supremum over $|x|=\rho^j$ gives
$|P_j|\rho^j\le C(K+1)\rho^{j(1+\al')}$, i.e.\
$|P_j|\le C(K+1)\rho^{j\al'}$; conclude by \eqref{eq:bj}.
\end{proof}

\subsubsection*{Step 5: the iteration theorem}
\begin{theorem}[Campanato iteration at flat points]\label{thm:E4}
Let $2\le p<\frac2{1-s}$ and let $\al',\rho,\varepsilon_0$ be as in
Lemma~\ref{lem:E2} with $B:=B_*$ from Lemma~\ref{lem:E3}. Let $V$ satisfy
$\fpl{V}=f$ weakly in $B_1$, $\|V\|_{L^\infty(B_1)}\le1$,
$\Tail(V;0,1)\le1$, the flatness \eqref{eq:flat} at $0$, and
\[
  \|f\|_{L^\infty(B_1)}\ \le\ \varepsilon_0 .
\]
Then there is an affine $\ell_\infty$ \textnormal{(}with
$\nabla\ell_\infty=P_\infty$, $|P_\infty|\le C$; under \eqref{eq:flat},
$P_\infty=0$\textnormal{)} such that
\[
  \sup_{B_r}|V-\ell_\infty|\ \le\ C\,r^{1+\al'}\qquad(0<r\le\tfrac12) :
\]
$V$ is $C^{1,\al'}$ at $0$ with a uniform jet estimate. If \eqref{eq:flat}
holds at every point of a subset $E\subset B_{1/2}$, the estimate holds
uniformly at every point of $E$.
\end{theorem}
\begin{proof}
Induction on $j$. Base $j=0$: $L_0=V(0)$, valid by \eqref{eq:flat} with
$K\le1$ after normalization. Inductive step: given \eqref{eq:excess-j},
Step~3 puts $V_j$ in the setting of Lemma~\ref{lem:E2} with shift $b_j$,
$|b_j|\le B_*$ by Lemma~\ref{lem:E3}, and right-hand side $f_j$ with
$\|f_j\|_\infty\le\|f\|_\infty\le\varepsilon_0$ by \eqref{eq:fj}
\textnormal{(}the factor is $\le1$\textnormal{)}. Lemma~\ref{lem:E2}
produces an affine correction realizing \eqref{eq:excess-j} at $j+1$ after
undoing the normalization. The excess chain and \eqref{eq:slope-tel} give
the stated Campanato conclusion by the usual telescoping; the flatness
\eqref{eq:flat} forces $P_\infty=0$ \textnormal{(}Lemma~\ref{lem:E3} gives
$P_j\to0$\textnormal{)}.
\end{proof}

\begin{remark}[Honest scope of Theorem~\ref{thm:E4}]\label{rem:E4-limits}
\textnormal{(i)} The flatness hypothesis \eqref{eq:flat} is \emph{strong}:
it presumes sup-flatness at the $C^{1,\al'}$ rate. This is exactly what the
blow-up normalization supplies at branching points \textnormal{(}the growth
caps of the $\theta$-device\textnormal{)}, so the theorem applies where we
need it; but Theorem~\ref{thm:E4} is \emph{not} an unconditional interior
$C^{1,\al'}$ estimate for $\fpl{V}=f$. \textnormal{(ii)} At non-flat
points, $|b_j|\to\infty$ and the iteration exits the bounded-shift regime;
there the natural continuation is the large-slope regime of~\cite{GJS}
\textnormal{(}their stages 2--3: gradient close to a fixed nonzero vector,
uniformly elliptic linearization\textnormal{)}, which we do \emph{not}
extract here. \textnormal{(iii)} The telescoped exterior-class bookkeeping
in Step~3 \textnormal{(}class-\textnormal{(A)} preservation with improving
tails\textnormal{)} is stated with a computation sketch, not in full
detail. \textnormal{(iv)} Nothing here touches
Hypothesis~\ref{hyp:L}: the iteration supplies the \emph{compactness and
flatness-preservation} inputs of the scheme, not the Liouville property.
\end{remark}

\subsection{Why this matters for the blow-up scheme}
In the perturbative (excess-decay) iteration, one approximates the blow-up
$v$ at scale $\rho^j$ by affine functions $\ell_j$ and studies
$w_j:=(v-\ell_j)(\rho^j\cdot)/\rho^{j(1+\al')}$. For $p\neq2$ the function
$w_j$ does \emph{not} solve the original equation; it solves
$A_{b_j}w_j=f_j$ with $b_j$ the accumulated affine slope and $f_j$ inheriting
smallness from the dead-core right-hand side
\textnormal{(}Proposition~\ref{prop:homog}\textnormal{)} \emph{and} from the
subcritical normalization: since $1+\al'\le\frac{sp}{p-1}$, the rescalings
remain tail-admissible, in contrast with every attempt at the supercritical
exponent $\beta$. Proposition~\ref{prop:P1} supplies exactly the
compactness/limit-identification for this iteration, uniformly in the shift;
Proposition~\ref{prop:P2A} supplies the decay of the limiting profile that
the iteration transfers back to $w_j$ --- and, by the conjugation mechanism,
this input is now \emph{proved}, not hypothesized, for the class
\textnormal{(A)} functions the iteration produces. Together they would give
uniform $C^{1,\al'}$ estimates for blow-ups with vanishing right-hand side
--- the input denoted ``$C^1_{loc}$-compactness'' in
Assumption~\ref{ass:compact} --- and thereby also the seminorm normalization
that feeds the unit-scale nondegeneracy mechanism of the Liouville section.
The iteration is carried out, at flat points, in
\S\ref{ssec:excess} (Theorem~\ref{thm:E4}); its scope and the non-flat
regime are delimited in Remark~\ref{rem:E4-limits}.

\begin{remark}[Limitations: exactly what remains unproved here]
\label{rem:P1-limits}
\textnormal{(i)} The class \textnormal{(B)} shifted estimate
\textnormal{(}Hypothesis P2$'$ of Remark~\ref{rem:P2status}\textnormal{)}
is unproved; its expected proof is
an adaptation, not a citation, of~\cite{GJS}. \textnormal{(ii)} The
excess-decay iteration is carried out at \emph{flat points} in
\S\ref{ssec:excess}; the non-flat (large-slope) regime remains an
extraction from~\cite{GJS}. \textnormal{(iii)} Strong $W^{s,p}_{loc}$
convergence of $v_k$, while plausibly available through the
$(S_+)$-property, is neither proved nor used. \textnormal{(iv)} Nothing in
this section addresses the degenerate-kernel Liouville
\textnormal{(}Hypothesis~\ref{hyp:L}\textnormal{)}, which remains the
principal open input of the main theorem.
\end{remark}

%======================================================================
\section{The Liouville step}\label{sec:liouville}
%======================================================================
The blow-up limit, if it exists and solves $\fpl{v_0}=0$, must be classified
among entire $(s,p)$-harmonic functions with a vanishing first jet. Both
statements below are \emph{conditional}.

\subsection{Direct rescaling: a global tail hypothesis}
\begin{lemma}[Conditional Liouville, direct route]\label{lem:liouville-cond}
Let $v$ be $(s,p)$-harmonic in $\R^n$ with $v(0)=|Dv(0)|=0$ and
$\beta<1+\al_0$. Suppose the rescalings $v_R(x):=v(Rx)/R^{\beta}$, $R\ge1$,
satisfy the uniform admissibility bound
\begin{equation}\label{eq:tail-assumption}
  \|v_R\|_{L^\infty(B_2)}+\Tail(v_R;0,2)\le M_0\qquad(R\ge1).
\end{equation}
Then $v\equiv0$.
\end{lemma}
\begin{proof}
Each $v_R$ is $(s,p)$-harmonic. By Lemma~\ref{lem:gjs} and
\eqref{eq:tail-assumption}, $\|v_R\|_{C^{1,\al_0}(B_1)}\le CM_0$; since
$v_R(0)=|Dv_R(0)|=0$, $|v_R(x)|\le CM_0|x|^{1+\al_0}$ on $B_1$. For fixed $z$
and $R>2|z|$, $\frac{|v(z)|}{R^{\beta}}=|v_R(z/R)|\le CM_0|z/R|^{1+\al_0}$, so
$|v(z)|\le CM_0|z|^{1+\al_0}R^{\beta-(1+\al_0)}\to0$ since $\beta<1+\al_0$.
\end{proof}

\begin{remark}[Why \eqref{eq:tail-assumption} is not cosmetic]\label{rem:tail}
A pointwise growth bound $|v(x)|\le C(1+|x|)^{\beta}$ does \emph{not} imply
\eqref{eq:tail-assumption}: the tail of $v_R$ scales like
$\int^\infty R^{\beta(p-1)-sp-1}dR$, finite only if $\beta(p-1)<sp$, whereas
$\beta(p-1)-sp=\frac{\gamma sp}{p-1-\gamma}>0$ for every $\gamma>0$. So the
direct route genuinely requires \eqref{eq:tail-assumption}. In the linear case
$p=2$ one bypasses it by working with differences, whose growth is one order
lower; for $p\neq2$ differences do not solve the homogeneous equation, the
obstruction addressed next.
\end{remark}

\subsection{Increment route: a conditional Liouville lemma}
By Proposition~\ref{prop:linincr}, $w^h=v(\cdot+h)-v$ solves the linear
equation $L_{K_h}w^h=0$; its growth is one order below that of $v$. The
relevant tail for this \emph{linear} equation carries the kernel coefficient
$K_h(x,y)\sim|v(y)|^{p-2}$ in the far field, so finiteness requires
$\beta(p-1)<sp+1$, not $(\beta-1)(p-1)<sp$.

\begin{remark}[The increment tail condition]\label{rem:tailcond}
For $|w^h(y)|\sim|y|^{\beta-1}$ and $K_h(x,y)|y|^{-n-sp}\sim
|y|^{\beta(p-2)-n-sp}$, the integral $\int_{|y|>1}|w^h(y)|K_h(x,y)|y|^{-n-sp}dy$
converges iff $(\beta-1)+\beta(p-2)-sp<0$, i.e.\ $\beta(p-1)<sp+1$, which is
\eqref{eq:tailcond}: $\gamma<\frac{p-1}{1+sp}$. This is consistent with the
$\mathrm{Tail}_{p-1,sp+1}$ that appears in the linearized estimates of~\cite{GJS}.
\end{remark}

The missing global input deserves a name and a precise statement.

\begin{hypothesis}[Degenerate-kernel Liouville property]\label{hyp:L}
Let $v_0$ be an entire function in the admissible class \textnormal{(}growth
$|v_0(x)|\le C(1+|x|)^{\beta}$, tail condition \eqref{eq:tailcond}\textnormal{)}
and let $L_{0,h}$ denote the linearized operator with kernel
$K_0^h(x,y)=a_0^h(x,y)|x-y|^{-n-sp}$, where $a_0^h$ is the increment
coefficient of Corollary~\ref{cor:incr-weak} built from $v_0$. \emph{We say
that Hypothesis \textnormal{(L)} holds if}: whenever $W\in C^0(\R^n)$
satisfies, weakly,
\[
  L_{0,h}W=0\ \text{ in }\R^n,
  \qquad |W(x)|\le C\,(1+|x|)^{\delta}\ \text{ for some }0<\delta<1,
\]
then $W$ is constant.
\end{hypothesis}

\noindent The coefficient $a_0^h$ may vanish (Remark~\ref{rem:order}), so
Hypothesis~(L) does \emph{not} follow from the uniformly elliptic nonlocal
Liouville theory \cite{FRO,Serra}; it is exactly the statement those theories
would give if uniform ellipticity held. The scale-uniform H\"older hypothesis
$(\star)$ below implies Hypothesis~(L) by the rescaling argument in the proof
of Theorem~\ref{thm:liouville-incr}; conversely (L) is the minimal form needed
to close the contradiction scheme of \S\ref{sec:growth}.

\begin{theorem}[Conditional Liouville, increment route]\label{thm:liouville-incr}
Let $p\ge2$, $s>1-\frac2p$, and let $v\in C^{1,\al_0}_{loc}(\R^n)$ be entire
$(s,p)$-harmonic with $v(0)=|Dv(0)|=0$, growth $|v(x)|\le C(1+|x|)^{\beta}$ and
$|Dv(x)|\le C(1+|x|)^{\beta-1}$, with $1<\beta<1+\asp$ and
$\beta(p-1)<sp+1$. Assume:
\begin{itemize}[leftmargin=2em]
\item[\textnormal{(ND)}] $v$ is \emph{nondegenerate}: $Dv\not\equiv0$ on any
open set, and on every compact subset of $\{Dv\neq0\}$ the kernel $K_h$ is
uniformly elliptic of order $sp-p+2$;
\item[$(\star)$] the local H\"older estimate of Lemma~\ref{lem:gjs} for
$L_{K_h}$ holds \emph{scale-uniformly}: there is $\asp\in(0,1)$ such that, for
the rescalings $w_R:=w^h(R\cdot)/R^{\beta-1}$ and centers in $\{Dv\neq0\}$,
$[w_R]_{C^{\asp}(B_{1/2})}\le C$ uniformly in $R\ge1$.
\end{itemize}
Then every increment $w^h$ is constant; hence $v$ is affine, and the vanishing
jet gives $v\equiv0$.
\end{theorem}
\begin{proof}
Fix $h$ and write $w=w^h$, $\beta'=\beta-1<\asp$. By $(\star)$,
$[w]_{C^{\asp}(B_{R/2})}=R^{\beta'-\asp}[w_R]_{C^{\asp}(B_{1/2})}\le
CR^{\beta'-\asp}\to0$ as $R\to\infty$, since $\beta'<\asp$. Hence
$[w]_{C^{\asp}(\R^n)}=0$, so $w$ is constant. (No translation invariance of the
kernel is used in this step; (ND) is what makes $(\star)$ meaningful across
centers.) Thus $v(\cdot+h)-v\equiv c(h)$; the cocycle identity
$c(h_1+h_2)=c(h_1)+c(h_2)$ and continuity give $c(h)=b\cdot h$, while
$c(h)=v(h)$ has a double zero at $0$, so $b=0$ and $v\equiv$ const $=0$.
\end{proof}

\begin{remark}[The cap is $\beta<1+\asp$, not $\beta<2$]\label{rem:incr-cap}
Two points must be stated honestly. First, $(\star)$ is the genuinely missing
input: \cite{BLS,GJS} prove the \emph{local} H\"older estimate
(Lemma~\ref{lem:gjs}) and use it to bootstrap the regularity of a given
solution, but they do \emph{not} prove the global, scale-uniform Liouville
property used above. Second, with only a $C^{\asp}$ (H\"older) estimate
available for the linearized equation, the rescaling forces the cap
$\beta-1<\asp$, i.e.\ $\beta<1+\asp$. The stronger cap $\beta<2$ would require a
$C^{1,\asp}$ estimate for the increment --- equivalently $C^{2,\asp}$ for the
$p$-Laplacian --- which does not exist for $p\neq2$. The value $\beta<2$ is
special to $p=2$, where the increment is $s$-harmonic and smooth. We therefore
write the cap as $\beta<1+\asp$ throughout.
\end{remark}

\begin{remark}[Nonemptiness]\label{rem:nonempty}
Under \eqref{eq:gjs-range} the constraints $\beta>1$, $\gamma<\frac{p-1}{1+sp}$,
and $\beta<1+\asp$ (any $\asp>0$) define a nonempty $\gamma$-interval
\[
  \max\Big\{0,\,p-1-sp\Big\}<\gamma<
   \min\Big\{\tfrac{p-1}{1+sp},\ (p-1)-\tfrac{sp}{1+\asp}\Big\},
\]
and the interval is nonempty \emph{iff} $s>1-\frac2p$ (equivalently
$p<\frac2{1-s}$). Indeed $\big(\tfrac{p-1}{1+sp}-(p-1-sp)\big)(1+sp)
=sp\,(sp-p+2)$, positive iff $sp-p+2>0$. At $p=2$ the tail condition is
$\gamma<\frac1{1+2s}$, matching~\cite{PTU}.
\end{remark}

%======================================================================
\subsection{A scale-dichotomy route to the degenerate Liouville property}
\label{ssec:dichotomy}
The remaining obstacle to Hypothesis~\ref{hyp:L} is that the coercivity of
$K_0^h$ is needed at \emph{every} scale, while the blow-up normalization
controls the profile only at unit scale. This subsection formulates a
finite-scale dichotomy that may replace the global statement. Nothing here
proves Hypothesis~\ref{hyp:L}; the point is to reduce it to two individually
tractable regimes plus one explicitly open composition step.

\subsubsection*{The scale excess}
Fix $\al'\in(0,\al_0)$ \textnormal{(}$\al_0$ from
Proposition~\ref{prop:P2A}\textnormal{)} and let $v_0$ be an entire profile
of the blow-up scheme, normalized so that the growth caps give
\begin{equation}\label{eq:caps}
  \mathcal D(R):=R^{\,1+\al'-\beta}\,[v_0]_{C^{1,\al'}(B_R)}\ \le\ 1
  \quad(R\ge1),
  \qquad
  \mathcal D(1)\ \ge\ \tfrac12 .
\end{equation}
$\mathcal D$ is the natural scale quantity: it is dimensionless under the
$\beta$-rescaling $v_0\mapsto v_0(R\cdot)/R^{\beta}$, it is monotone
comparable across dyadic scales \textnormal{(}nested seminorms:
$\mathcal D(R)\le 2^{\beta-1-\al'}\mathcal D(2R)$\textnormal{)}, and its two
extreme behaviors are exactly the two mechanisms available.

\subsubsection*{Good scales}
Call $R$ a \emph{$\delta_0$-good scale} if $\mathcal D(R)\ge\delta_0$. The
normalization \eqref{eq:caps} makes $R=1$ good for any
$\delta_0\le\frac12$: the dichotomy always has an anchor.

\begin{lemma}[Seminorm-to-directional nondegeneracy at good scales]
\label{lem:interp-paper}
Let $\bar v_R:=v_0(R\cdot)/R^{\beta}$ and suppose
$\|\bar v_R\|_{C^{1,\al_0}(B_2)}\le\Lambda$
\textnormal{(}supplied by Proposition~\ref{prop:P2A} under the growth
caps\textnormal{)} and $R$ is $\delta_0$-good, so that
$[\bar v_R]_{C^{1,\al'}(B_1)}\ge\delta_0$. Then there are a unit vector
$e_R$ and constants
\[
  c_1=\tfrac18\,\delta_0\,(2\Lambda/\delta_0)^{-\frac{\al'}{\al_0-\al'}},
  \qquad \mu=\mu(n,\Lambda,c_1)>0,
\]
such that $\big|\{x\in B_2:\ D_{e_R}\bar v_R\ge c_1\}\big|\ge\mu|B_2|$.
\end{lemma}
\begin{proof}
The seminorm bound gives $x,y\in B_1$ with
$|\nabla\bar v_R(x)-\nabla\bar v_R(y)|\ge\delta_0|x-y|^{\al'}$; the
$C^{1,\al_0}$ bound gives
$|\nabla\bar v_R(x)-\nabla\bar v_R(y)|\le\Lambda|x-y|^{\al_0}$. Hence
$|x-y|\ge(\delta_0/2\Lambda)^{1/(\al_0-\al')}=:d_0$
\textnormal{(}the two-exponent gap forbids concentration\textnormal{)}, so
$|\nabla\bar v_R|\ge\frac14\delta_0d_0^{\al'}=2c_1$ at one of the two
points, call it $x_0$; set $e_R=\nabla\bar v_R(x_0)/|\nabla\bar v_R(x_0)|$.
By the $C^{0,\al_0}$ continuity of $\nabla\bar v_R$,
$D_{e_R}\bar v_R\ge c_1$ on $B_{r_1}(x_0)$ with
$r_1=(c_1/\Lambda)^{1/\al_0}$, and $\mu=(r_1/4)^n$.
\end{proof}

\noindent On a good scale, Lemma~\ref{lem:interp-paper} feeds the
cone-nondegeneracy mechanism \textnormal{(}the kernel lower bound
$a_0^h(x,y)\ge\lambda|x-y|^{p-2}$ on a positive-measure set of pairs along
the direction $e_R$\textnormal{)}, which is exactly the coercivity
assumption of the linearized H\"older estimate of~\cite[\S7]{GJS}. Granting
that estimate --- with the far field carried as a vanishing-oscillation
datum by the truncation mechanism of \S\ref{sec:prelim}, under
$\gamma<\frac{p-1}{1+sp}$ --- one obtains: \emph{there are
$\rho_0,\vartheta\in(0,1)$, depending on $\delta_0$ but not on $R$, with}
\begin{equation}\label{eq:good-decay}
  \operatorname*{osc}_{B_{\rho_0R}}\frac{W^h}{R^{\beta-1}}
  \ \le\ (1-\vartheta)\operatorname*{osc}_{B_{R}}\frac{W^h}{R^{\beta-1}}
  \qquad\text{at every $\delta_0$-good scale }R .
\end{equation}
We emphasize that \eqref{eq:good-decay} is \emph{conditional} on the
applicability of the \cite[\S7]{GJS} machinery with datum; this is a
packaging step, not a new estimate, but it is not written out here.

\subsubsection*{Bad scales}
Call $R$ \emph{$\delta_0$-bad} if $\mathcal D(R)<\delta_0$. Then
jet-to-growth \textnormal{(}$v_0(0)=0$, vanishing $1$-jet in the sup
sense\textnormal{)} gives directly
\begin{equation}\label{eq:bad-small}
  \sup_{B_R}|v_0|\ \le\ \delta_0\,R^{\beta},
  \qquad
  \sup_{B_R}|W^h|\ \le\ C|h|\,\delta_0\,R^{\beta-1}:
\end{equation}
at a bad scale the increment is \emph{automatically} small relative to its
growth cap --- no ellipticity is needed.

\subsubsection*{The dichotomy lemma}
\begin{lemma}[Conditional scale dichotomy]\label{lem:dichotomy}
Let $v_0$ be as above and assume the good-scale decay
\eqref{eq:good-decay}. Set $\varepsilon_*:=\frac{\beta\gamma}{p-1}$, so that
$\beta-\varepsilon<\frac{sp}{p-1}$ iff $\varepsilon>\varepsilon_*$. Then:
\begin{itemize}[leftmargin=2em]
\item[\textnormal{(i)}] \textbf{(Pure good.)} If there is $\delta_0>0$ such
that all scales $R\ge1$ are $\delta_0$-good, then \eqref{eq:good-decay}
iterates along $R_j=\rho_0^{-j}$ and yields
$[W^h]_{C^{0,\sigma}}$-decay with
$\sigma=\frac{\log(1-\vartheta)^{-1}}{\log\rho_0^{-1}}$; if
$\beta-1<\sigma$, every increment is constant, $v_0$ is affine, and the
vanishing jet gives $v_0\equiv0$.
\item[\textnormal{(ii)}] \textbf{(Pure bad, quantitative.)} If
$\mathcal D(R)\le C R^{-\varepsilon}$ for all $R\ge R_0$ with
$\varepsilon>\varepsilon_*$, then $|v_0(x)|\le C(1+|x|)^{\beta-\varepsilon}$
by \eqref{eq:bad-small} applied dyadically, the rescalings
$v_0(R\cdot)/R^{\beta-\varepsilon}$ satisfy the uniform admissibility
\eqref{eq:tail-assumption} \textnormal{(}subcritical growth:
$(\beta-\varepsilon)(p-1)<sp$\textnormal{)}, and the \emph{direct}
Liouville route \textnormal{(}Lemma~\ref{lem:liouville-cond}, which needs
no linearized kernel at all\textnormal{)} gives $v_0\equiv0$.
\item[\textnormal{(iii)}] \textbf{(Mixed.)} If neither regime holds ---
good and bad scales alternate, with $\mathcal D$ neither bounded below nor
decaying at rate $\varepsilon_*$ --- the two mechanisms must be composed,
and \emph{this composition is open}; see
Remark~\ref{rem:dichotomy-limits}.
\end{itemize}
\end{lemma}
\begin{proof}[Proof sketch]
(i): iterate \eqref{eq:good-decay}; the anchor is $R=1$
\textnormal{(}always good\textnormal{)}; the H\"older seminorm decay at all
scales upgrades to the Liouville conclusion by the standard dyadic
telescoping, exactly as in Theorem~\ref{thm:liouville-incr}, whose
hypothesis $(\star)$ is precisely what \eqref{eq:good-decay}-at-all-scales
provides. (ii): for $2^j\le|x|<2^{j+1}$, jet-to-growth with the seminorm
bound at scale $2^{j+1}$ gives
$|v_0(x)|\le\mathcal D(2^{j+1})\,|x|^{\beta}\le C|x|^{\beta-\varepsilon}$;
the threshold $\varepsilon>\varepsilon_*$ is exactly what makes
$(\beta-\varepsilon)(p-1)<sp$, i.e.\ the rescalings' tails converge with a
uniform bound, which is hypothesis \eqref{eq:tail-assumption}; conclude by
Lemma~\ref{lem:liouville-cond} applied with exponent $\beta-\varepsilon$
\textnormal{(}the vanishing jet persists\textnormal{)}.
\end{proof}

\subsubsection*{The mixed regime: a bridge inequality and a combined
criterion}
The two branches act on different objects --- good scales decay the
\emph{increment}, bad scales shrink the \emph{profile}. The following
elementary inequality connects them: the increment can never be worse than
the scale excess.

\begin{lemma}[Bridge inequality]\label{lem:bridge}
Let $v_0$ be a blow-up profile as above, $C^1$ at the flat origin with
$\nabla v_0(0)=0$ \textnormal{(}available at flat points by
Theorem~\ref{thm:E4}\textnormal{)}. Then, for $0<|h|\le1$ and $R\ge1$,
\[
  X(R):=\frac{\operatorname{osc}_{B_R}W^h}{|h|\,R^{\beta-1}}
  \ \le\ C\,\mathcal D(2R) .
\]
\end{lemma}
\begin{proof}
Since $\nabla v_0(0)=0$,
$|\nabla v_0(x)|\le[v_0]_{C^{1,\al'}(B_{2R})}|x|^{\al'}
\le\mathcal D(2R)(2R)^{\beta-1-\al'}|x|^{\al'}
\le C\mathcal D(2R)R^{\beta-1}$ for $|x|\le R+1$. The mean value theorem
gives $\operatorname{osc}_{B_R}W^h\le2|h|\sup_{B_{R+1}}|\nabla v_0|$.
\end{proof}

\begin{proposition}[Combined criterion; conditional]\label{prop:combined}
Assume the good-scale decay \eqref{eq:good-decay} with parameters
$(\rho_0,\vartheta)$, and let $\sigma$ denote the resulting H\"older
exponent, assumed to satisfy $\sigma>\beta-1$. For $R\ge\rho\ge1$ let
$\#G(\rho,R)$ be the number of $\delta_0$-good dyadic scales in
$[\rho,R]$, and set
\[
  \nu:=\liminf_{R\to\infty}\frac{\#G(1,R)}{\log_2R},
  \qquad
  \kappa:=\liminf_{R\to\infty}\frac{\log\mathcal D(R)^{-1}}{\log R},
  \qquad
  c_\vartheta:=\frac{\log(1-\vartheta)^{-1}}{\log2} .
\]
If
\begin{equation}\label{eq:window-out}
  \nu\,c_\vartheta+\kappa\ >\ \beta-1
  \qquad\text{or}\qquad
  \kappa\ >\ \varepsilon_*=\frac{\beta\gamma}{p-1},
\end{equation}
then $v_0\equiv0$ \textnormal{(}and in particular Hypothesis~\ref{hyp:L}
holds for the profile $v_0$\textnormal{)}.
\end{proposition}
\begin{proof}[Proof sketch]
If $\kappa>\varepsilon_*$, branch (ii) of Lemma~\ref{lem:dichotomy}
applies. Otherwise, fix $\rho\ge1$ and run the good-scale decay
\eqref{eq:good-decay} \emph{downward} from a large scale $R$, anchoring
with the bridge inequality at $R$:
\[
  \operatorname{osc}_{B_\rho}W^h
  \ \le\ (1-\vartheta)^{\#G(\rho,R)}\,\operatorname{osc}_{B_R}W^h
  \ \le\ (1-\vartheta)^{\#G(\rho,R)}\,C\,\mathcal D(2R)\,R^{\beta-1}|h| ,
\]
bad scales contributing no growth to the chain since
$\operatorname{osc}_{B_r}W^h$ is monotone in $r$. Taking logarithms, the
right-hand side tends to $0$ along a sequence $R\to\infty$ precisely when
$\nu c_\vartheta+\kappa>\beta-1$. Hence $W^h$ is constant for every $h$,
$v_0$ is affine, and the vanishing jet gives $v_0\equiv0$.
\end{proof}

\begin{remark}[The residual window, and a proposed attack]
\label{rem:window}
The mixed regime is thereby reduced to the explicit \emph{window}
\begin{equation}\label{eq:window}
  \kappa\ \le\ \varepsilon_*
  \qquad\text{and}\qquad
  \nu\,c_\vartheta+\kappa\ \le\ \beta-1 :
\end{equation}
profiles whose scale excess decays, but slowly, with good scales too
sparse. Three structural facts confine the window further:
\textnormal{(a)} the one-sided dyadic comparability
$\mathcal D(2R)\ge2^{-(\beta-1-\al')}\mathcal D(R)$ plus the normalization
$\mathcal D(1)\ge\frac12$ force an \emph{initial good block} of length
$\gtrsim\log(1/\delta_0)$; \textnormal{(b)} by the bridge inequality, in
the window the increments are already uniformly small relative to their
caps ($X\le C\mathcal D\le C\delta_0$ at bad scales); \textnormal{(c)} the
window pins $\mathcal D$ between two rates. Fact (c) suggests a
\emph{second blow-up}: along window scales $R_j$, renormalize
$v_j:=v_0(R_j\cdot)/(\mathcal D(R_j)R_j^{\beta})$; any limit has excess
pinned at unit size at all scales --- i.e.\ \emph{all scales good} --- and
the pure-good branch (i) applies to it. Transferring the conclusion back
to $v_0$ across the double limit is the unresolved step; we record this as
the proposed attack, not as a proof.
\end{remark}

\subsubsection*{The second blow-up at transition scales}
We now carry out the program of Remark~\ref{rem:window} as far as it goes,
and isolate exactly where it stops. Throughout, $v_0$ is a window profile:
flat at $0$ \textnormal{(}$v_0(0)=0$, $\nabla v_0(0)=0$, by
Theorem~\ref{thm:E4}\textnormal{)}, $(s,p)$-harmonic in the profile sense,
with caps $\mathcal D\le1$, anchor $\mathcal D(1)\ge c_0$, and
\eqref{eq:window}.

\begin{lemma}[Selection of transition scales]\label{lem:select}
There exist $R_j\to\infty$ and $C_\sharp\ge1$ with
\begin{equation}\label{eq:pin}
  \mathcal D(R_jt)\ \le\ C_\sharp\,\mathcal D(R_j)
  \qquad\text{for all }t\ge1,\ j\in\mathbb N .
\end{equation}
\end{lemma}
\begin{proof}
If $\liminf_{R\to\infty}\mathcal D(R)>0$, all large scales are
$\delta_0$-good for small $\delta_0$ and the pure-good branch of
Lemma~\ref{lem:dichotomy} applies directly; the lemma is then not needed.
If $m_\infty:=\limsup\mathcal D>0=\liminf\mathcal D$, choose $R_j\to\infty$
with $\mathcal D(R_j)\ge m_\infty/2$; then
$\mathcal D(R_jt)\le m_\infty+o(1)\le(2+o(1))\mathcal D(R_j)$. If
$\mathcal D(R)\to0$, let $\varepsilon_j\downarrow0$ and take the
\emph{last-exit scales} $R_j:=\sup\{R\ge1:\mathcal D(R)\ge\varepsilon_j\}$
\textnormal{(}finite; $\mathcal D$ is continuous in $R$\textnormal{)}: then
$\mathcal D(R_j)=\varepsilon_j$ and $\mathcal D(R)<\mathcal D(R_j)$ for all
$R>R_j$, i.e.\ \eqref{eq:pin} with $C_\sharp=1$.
\end{proof}

\begin{lemma}[Second blow-up: compactness and nontriviality]\label{lem:z}
Set $z_j(x):=v_0(R_jx)/(\mathcal D(R_j)R_j^{\beta})$ \textnormal{(}no
affine subtraction: the jet of $v_0$ at $0$ vanishes, so $P_j=0$ is the
correct normalization and no shifted operator appears\textnormal{)}. Then:
\begin{itemize}[leftmargin=2em]
\item[\textnormal{(i)}] $[z_j]_{C^{1,\al'}(B_t)}
  =\frac{\mathcal D(R_jt)}{\mathcal D(R_j)}\,t^{\beta-1-\al'}
  \le C_\sharp t^{\beta-1-\al'}$ for $t\ge1$, and
  $[z_j]_{C^{1,\al'}(B_1)}=1$ exactly;
\item[\textnormal{(ii)}] $z_j$ is $(s,p)$-harmonic in the same profile
  sense as $v_0$ \textnormal{(}homogeneous rescaling, zero right-hand
  side\textnormal{)}, with vanishing jet at $0$;
\item[\textnormal{(iii)}] assume in addition the profile-level interior
  estimate $\|z_j\|_{C^{1,\al_0}(B_2)}\le\Lambda$ with $\al_0>\al'$
  \textnormal{(}the same conditional input used throughout this section:
  the \cite{GJS}-type bound for profiles, with the far field as
  datum\textnormal{)}. Then, for every $\al''\in(0,\al')$, along a
  subsequence $z_j\to z_\infty$ in $C^{1,\al''}_{loc}(\R^n)$, and
\[
  [z_\infty]_{C^{1,\al''}(B_1)}\ \ge\
  \tfrac12\,d_0^{\,\al'-\al''},\qquad
  d_0:=(2\Lambda)^{-\frac1{\al_0-\al'}} ,
\]
so the limit is nontrivial; it has vanishing jet at $0$ and caps
$\mathcal D_{z_\infty}(t)\le C_\sharp$ for all $t\ge1$.
\end{itemize}
\end{lemma}
\begin{proof}
(i) is the scaling identity for seminorms plus \eqref{eq:pin}. (ii) is the
homogeneity of $J_p$; no subtraction is performed, so no shift arises.
(iii): (i) bounds $\{z_j\}$ in $C^{1,\al'}(B_t)$ for each $t$;
Arzel\`a--Ascoli in the compact embedding
$C^{1,\al'}\hookrightarrow C^{1,\al''}$ gives the convergence --- \emph{no
equation is used for compactness}. Nontriviality is the two-exponent-gap
mechanism of Lemma~\ref{lem:interp-paper}: the pair $x,y\in B_1$
near-attaining $[\nabla z_j]_{C^{0,\al'}(B_1)}=1$ satisfies
$\tfrac12|x-y|^{\al'}\le|\nabla z_j(x)-\nabla z_j(y)|\le\Lambda|x-y|^{\al_0}$,
forcing $|x-y|\ge d_0$: concentration at small pair-distances is forbidden
by the $C^{1,\al_0}$ bound, \emph{not} by interpolation alone
\textnormal{(}for arbitrary functions the $\al''$-seminorm can indeed
concentrate away\textnormal{)}. Hence
$[\nabla z_j]_{C^{0,\al''}(B_1)}\ge|\nabla z_j(x)-\nabla z_j(y)|\,|x-y|^{-\al''}
\ge\tfrac12 d_0^{\al'-\al''}$, and strong $C^{1,\al''}(B_1)$ convergence
transfers this to $z_\infty$.
\end{proof}

\begin{remark}[The transfer-back difficulty dissolves; the real missing
step]\label{rem:z-missing}
Two points, one positive and one negative.
\emph{Positive:} no delicate double-limit transfer to $v_0$ is needed. If
the pure-good branch applied to $z_\infty$ and forced its increments
constant, then $z_\infty$ would be affine, contradicting
$[z_\infty]_{C^{1,\al''}(B_1)}\ge c>0$ outright. The contradiction lives
entirely at the level of $z_\infty$; nontriviality is inherited
\emph{forward} by Lemma~\ref{lem:z}(iii).
\emph{Negative:} what fails is the \textbf{persistence of goodness}. The
selection \eqref{eq:pin} pins the excess of $z_\infty$ from \emph{above}
only; the lower pinning $\mathcal D(R_jt)\ge c\,\mathcal D(R_j)$ is false
in general --- in the last-exit case $\mathcal D$ strictly decays beyond
$R_j$, and the one-sided dyadic comparability gives only
$\mathcal D_{z_\infty}(t)\ge t^{-(\beta-1-\al')}$. Hence $z_\infty$ may
again have decaying excess at large scales, i.e.\ may itself be a window
profile: the second blow-up reproduces the class instead of exiting it.
\textbf{This --- a uniform lower bound on the excess of the second blow-up
limit at all scales --- is the exact missing step}, and iterating the
construction lacks a strictly decreasing quantity: precisely where a
monotonicity formula would be decisive \textnormal{(}available for $p=2$
via the extension; unknown for $p\neq2$\textnormal{)}.
\end{remark}

\begin{remark}[Complementarity with the weighted route]\label{rem:window-bdor}
The window has a feature that the weighted route (W) of \S\ref{sec:open}
can exploit: small $\kappa$ means $\mathcal D$ is \emph{slowly varying}, so
the natural weight $w=|\nabla v_0|^{p-2}\sim(\mathcal D(R)R^{\beta-1})^{p-2}$
has controlled ratios on dyadic annuli --- a large part of a Muckenhoupt
bound. What is missing for BDOR-admissibility is a \emph{lower average}
bound for $|\nabla v_0|^{p-2}$ on annuli \textnormal{(}nondegeneracy in
average; $\nabla v_0$ may still vanish on large portions\textnormal{)}.
Thus the combined criterion kills fast decay and dense good scales, while
the weighted route is best adapted exactly to the slowly-varying window ---
the two attacks are complementary, and the window is squeezed from both
sides. Neither claim is completed here.
\end{remark}

\subsubsection*{Persistence of good scales via a three-scales property}
The missing step of Remark~\ref{rem:z-missing} reduces, in its entirety, to
a single classical-flavoured inequality. We first record what is automatic.

\begin{lemma}[Automatic power lower bound]\label{lem:autopower}
For any profile $z$ with $\mathcal D_z(1)\ge c_0$,
\[
  \mathcal D_z(R)\ \ge\ c_0\,R^{-\eta_0},
  \qquad \eta_0:=\beta-1-\al'\qquad(R\ge1).
\]
\end{lemma}
\begin{proof}
$[z]_{C^{1,\al'}(B_R)}$ is nondecreasing in $R$;
$\mathcal D_z(R)=R^{-\eta_0}[z]_{C^{1,\al'}(B_R)}\ge R^{-\eta_0}c_0$.
\end{proof}

\noindent Thus the excess can never decay \emph{faster} than the fixed
power $R^{-\eta_0}$; the danger is decay to zero \emph{slower than every
power}. The following hypothesis excludes it.

\begin{hypothesis}[Three-scales property \textnormal{(H3S)}]\label{hyp:H3S}
For profiles $z$ as above \textnormal{(}entire, $(s,p)$-harmonic in the
profile sense, flat at $0$\textnormal{)}, the function
\[
  \tau\ \longmapsto\ \log\,[z]_{C^{1,\al'}(B_{e^\tau})}
\]
is convex on $[0,\infty)$ --- or quasi-convex up to additive errors
$\epsilon_j$ with $\sum\epsilon_j<\infty$ along dyadic scales.
\end{hypothesis}

\begin{theorem}[The window closes under \textnormal{(H3S)}]\label{thm:H3S}
Assume the good-scale packaging \eqref{eq:good-decay} with
$\sigma>\beta-1$, and Hypothesis~\ref{hyp:H3S}. Then no nontrivial window
profile exists; combined with Proposition~\ref{prop:combined}, Hypothesis
\ref{hyp:L} holds for all blow-up profiles.
\end{theorem}
\begin{proof}[Proof sketch]
Under \textnormal{(H3S)}, $\log\mathcal D_z$ is convex in $\log R$
\textnormal{(}convex minus linear\textnormal{)}, so the dyadic decay rates
$r_j:=\log_2\frac{\mathcal D_z(2^j)}{\mathcal D_z(2^{j+1})}$ are
nondecreasing, with limit $\kappa\ge0$. Trichotomy:

\emph{(i) $\inf_R\mathcal D_z>0$.} All scales are $\delta_0$-good for
small $\delta_0$; the pure-good branch of Lemma~\ref{lem:dichotomy}(i)
kills $z$.

\emph{(ii) $\mathcal D_z(R)\to0$ with $\kappa=0$: impossible.} Decay to
zero forces $\sum_jr_j=+\infty$, while $r_j$ nondecreasing with
$r_j\to\kappa=0$ forces $r_j\le0$ for all $j$ --- contradiction.
\emph{Sub-polynomial decay is excluded by convexity alone.}

\emph{(iii) $\kappa>0$: descent of the exponent.} Difference quotients of
convex functions converge locally uniformly, so along the transition
scales of Lemma~\ref{lem:select} the rates converge to $\kappa$ uniformly
on bounded $\log$-windows, and the second blow-up limit $z_\infty$ of
Lemma~\ref{lem:z} has \emph{exactly}
$\mathcal D_{z_\infty}(t)=t^{-\kappa}$: this is precisely the persistence
input missing in Remark~\ref{rem:z-missing}, supplied here by
\textnormal{(H3S)}. Consequently $z_\infty$ has exact growth exponent
$\beta':=\beta-\kappa<\beta$, and its excess \emph{relative to $\beta'$},
$t^{1+\al'-\beta'}[z_\infty]_{C^{1,\al'}(B_t)}$, is constant in $t$: all
scales are good at exponent $\beta'$. The increment machinery applies
verbatim at $\beta'$ \textnormal{(}the tail condition
$\beta'(p-1)<sp+1$ is inherited from $\beta'<\beta$; the pure-good
constraint weakens to $\sigma>\beta'-1$\textnormal{)}, and the pure-good
branch forces the increments of $z_\infty$ to be constant, hence
$z_\infty$ affine --- contradicting the nontriviality
$[z_\infty]_{C^{1,\al''}(B_1)}\ge c>0$ of Lemma~\ref{lem:z}(iii). One
descent step suffices; no iteration is needed.
\end{proof}

\begin{remark}[Status of \textnormal{(H3S)}; annular nondegeneracy; the
$A_2$ criterion]\label{rem:H3S-status}
\textnormal{(a)} \emph{Status.} For harmonic functions the convexity of
$\log\sup_{B_R}|u|$ is Hadamard's three-circles theorem, and seminorm
versions follow from interior estimates. For \emph{linear} $s$-harmonic
functions, frequency-function methods through the extension
\textnormal{(}Almgren monotonicity; cf.\ the unique-continuation
literature\textnormal{)} give doubling and three-spheres statements ---
for sup-norms, and by an adaptation that we do not carry out here, for the
seminorms used in \textnormal{(H3S)}. For the fractional $p$-Laplacian,
\textbf{no three-spheres or doubling inequality is known}; there is no
extension, no frequency function, and no unique-continuation theory. This
is now the precise frontier of the paper: Hypothesis~\ref{hyp:L} has been
reduced to \textnormal{(H3S)} \textnormal{(}plus the packaging
\eqref{eq:good-decay}\textnormal{)}.
\textnormal{(b)} \emph{Annular nondegeneracy at good scales is free:} if
$\mathcal D_z(R)\ge\delta_0$, Lemma~\ref{lem:interp-paper} gives a ball
$B_{r_1R}(x_R)\subset B_{2R}$ with $|\nabla z|\ge c_1R^{\beta-1}$, whence
\[
  \fint_{A_R}|\nabla z|^{p-2}\,dx\ \ge\ c\,\mu\,(c_1R^{\beta-1})^{p-2},
  \qquad A_R=B_{2R}\setminus B_R ;
\]
at bad scales such a bound is equivalent to the persistence problem
itself.
\textnormal{(c)} \emph{The $A_2$ criterion, made exact.} For the weighted
route the missing half is the \emph{inverse} average: $w=|\nabla z|^{p-2}$
satisfies the $A_2$ condition on $A_R$ iff
$\big(\fint_{A_R}w\big)\big(\fint_{A_R}w^{-1}\big)\le C$; the direct
average is controlled at good scales by (b) and from above by slow
variation, but $\fint_{A_R}|\nabla z|^{-(p-2)}$ requires the critical set
$\{\nabla z=0\}$ to be small with power-type vanishing. For local
$p$-harmonic functions in the plane this follows from quasiregularity of
the complex gradient \textnormal{(}Bojarski--Iwaniec\textnormal{)}; a
nonlocal analogue is \textbf{not known} in any dimension. The
inverse-average bound is the genuinely hard half of BDOR-admissibility.
\end{remark}

\subsubsection*{On the three-scales hypothesis: calibrations and substitutes}

\begin{lemma}[Norm transfer]\label{lem:normtransfer}
Under the standing profile interior estimates, for $R\ge1$,
\[
  M(R):=\|z\|_{L^\infty(B_R)}\le [z]_{C^{1,\al'}(B_R)}R^{1+\al'},
  \qquad
  [z]_{C^{1,\al'}(B_R)}\le C R^{-(1+\al')}M(2R),
\]
the first by the vanishing jet, the second by interior regularity applied
at scale $R$. Consequently \textnormal{(H3S)} for the seminorm and for the
sup norm $M$ are equivalent up to bounded additive errors in the
$\log$--$\log$ plane and a fixed radius doubling --- harmless for every use
made of \textnormal{(H3S)} above. The sup norm \textnormal{(}or the
spherical $L^2$ norm\textnormal{)} is the natural primary quantity.
\end{lemma}

\begin{remark}[Calibration at $p=2$: \textnormal{(H3S)} holds]
\label{rem:p2calib}
For $(-\Delta)^sz=0$ the Caffarelli--Silvestre extension $Z$ solves the
$A_2$-weighted equation $\mathrm{div}(y^{1-2s}\nabla Z)=0$ in
$\R^{n+1}_+$, with vanishing weighted Neumann datum on all of
$\{y=0\}$; the Almgren frequency
$N(R)=R\,\mathcal D_{\mathrm{ext}}(R)/H(R)$,
$H(R)=\int_{\partial B_R^+}y^{1-2s}Z^2$, is monotone nondecreasing
\textnormal{(}Caffarelli--Salsa--Silvestre/Fall--Felli-type; to be quoted
with precise hypotheses\textnormal{)}, and monotonicity of $N$ gives
convexity of $\log H$ in $\log R$ up to an explicit linear term:
\textnormal{(H3S)} holds \emph{exactly} for $H$. The transfer to $M(R)$
uses trace and doubling comparabilities standard in the
unique-continuation literature; we flag it as an adaptation to verify, not
a gap of principle. Thus at $p=2$ the trichotomy of
Theorem~\ref{thm:H3S} runs and the window closes in principle --- a
consistency check of the whole architecture. What fails for $p\neq2$: the
extension does not exist, the frequency requires the bilinear structure,
and spherical decompositions are linear tools.
\end{remark}

\begin{remark}[Sobering calibration: the local sibling is open]
\label{rem:localcalib}
For the \emph{local} $p$-Laplacian, three-spheres/doubling inequalities
and strong unique continuation are: known in the plane, via
quasiregularity of the complex gradient
\textnormal{(}Bojarski--Iwaniec; Hadamard three-circles with
distortion-modified exponents; isolated critical points with power
vanishing\textnormal{)}; and \textbf{open in dimension $n\ge3$} --- a
well-known problem, where even $|\{\nabla z=0\}|=0$ is not known in
general. \textnormal{(H3S)} for $(-\Delta_p)^s$ in general dimension would
therefore imply progress on a problem whose local version has resisted for
decades. Two mitigations: the profile class is far more special than
arbitrary solutions \textnormal{(}flatness, growth caps, two-sided excess
bounds\textnormal{)}, and only the substitutes below are needed; and the
cases $p=2$ \textnormal{(}above\textnormal{)} and $n=2$
\textnormal{(}quasiregular toolbox\textnormal{)} are realistic targets.
\end{remark}

\begin{remark}[Minimal substitutes for \textnormal{(H3S)}]
\label{rem:substitutes}
The full convexity is more than the proof uses. Two strictly weaker
statements suffice:
\begin{itemize}[leftmargin=2em]
\item[\textnormal{(S1)}] \emph{Polynomial-or-nothing with threshold:} if
$\mathcal D_z(R)\to0$ then $\mathcal D_z(R)\le CR^{-\varepsilon}$
eventually, for some $\varepsilon>\varepsilon_*=\frac{\beta\gamma}{p-1}$.
Then the \emph{direct} route \textnormal{(}branch (ii) of
Lemma~\ref{lem:dichotomy}\textnormal{)} closes the window with no second
blow-up and no pinning.
\item[\textnormal{(S2)}] \emph{Quasi-monotone rates:}
$r_{j+1}\ge r_j-\epsilon_j$ with $\sum\epsilon_j<\infty$, where
$r_j=\log_2\frac{\mathcal D_z(2^j)}{\mathcal D_z(2^{j+1})}$. This is the
weakest hypothesis under which the full trichotomy of
Theorem~\ref{thm:H3S}, including the exact pinning in case (iii), runs
verbatim.
\end{itemize}
Automatically true, for comparison: rates are bounded \emph{above}
($r_j\le\eta_0\log2$, Lemma~\ref{lem:autopower}); no lower
quasi-monotonicity is proved here. We also record why the soft routes
fail: Caccioppoli and reverse H\"older are \emph{inequalities}, while
convexity requires an \emph{identity}; Harnack for increments is circular
\textnormal{(}it is Hypothesis~\ref{hyp:L}\textnormal{)}; the classical
comparison proof of three-spheres superposes radial solutions linearly,
which $p\neq2$ forbids \textnormal{(}a quasi-superposition barrier
$(a^{p-1}+b^{p-1}r^{\lambda(p-1)})^{1/(p-1)}$ is untested and
speculative\textnormal{)}.
\end{remark}

\begin{remark}[The exact missing identity]\label{rem:pohozaev}
The monotonicity route reduces to a single unproved formula: a
Pohozaev--Rellich identity for the Gagliardo $p$-energy, i.e.\ an exact
expression for the derivative of
$R\mapsto R^{sp-n}\iint_{B_R\times B_R}
\frac{|z(x)-z(y)|^p}{|x-y|^{n+sp}}\,dx\,dy$
along the position vector field, generalizing the $p=2$ identity of
Ros-Oton--Serra. For $p\neq2$ no such identity is known; its discovery
would yield an Almgren-type frequency for $(-\Delta_p)^s$ and, through
Theorem~\ref{thm:H3S}, close this paper's program. We record it as the
sharpest formulation of what is missing.
\end{remark}

\begin{remark}[Exact weighted-route hypothesis]\label{rem:wadm}
The BDOR alternative requires precisely:
\begin{quote}
\textnormal{(W-adm)}: there are $C$ and infinitely many $R$ with
$\displaystyle\Big(\fint_{A_R}|\nabla z|^{p-2}\Big)
\Big(\fint_{A_R}|\nabla z|^{-(p-2)}\Big)\le C .$
\end{quote}
The direct factor is controlled \textnormal{(}below at good scales by
Remark~\ref{rem:H3S-status}(b), above by slow variation\textnormal{)}.
The inverse factor requires power-type smallness of
$\{|\nabla z|<t\}\cap A_R$; this is \emph{not} implied by
$C^{1,\al}$-regularity plus nontrivial excess \textnormal{(}gradients of
$C^{1,\al}$ functions may vanish on open sets\textnormal{)}, is open for
the profile class, and a nonlocal Bojarski--Iwaniec theorem is not known
in any dimension.
\end{remark}

\begin{remark}[Limitations]\label{rem:dichotomy-limits}
\textnormal{(a)} The good-scale decay \eqref{eq:good-decay} is conditional
on packaging the \cite[\S7]{GJS} linearized estimate with far-field datum;
this packaging is believed routine under $\gamma<\frac{p-1}{1+sp}$ but is
not written. Its H\"older exponent $\sigma$ is small and non-explicit, and
\emph{both} the pure-good branch and Proposition~\ref{prop:combined}
require $\sigma>\beta-1$: an implicit smallness condition on
$\beta-1$ \textnormal{(}i.e.\ on $\gamma-(p-1-sp)$\textnormal{)} that we
cannot quantify with current tools. \textnormal{(b)} Bad scales give
\emph{constant}-level improvement only; no mechanism in this paper
upgrades repeated smallness of $\mathcal D$ to a decay \emph{rate}, so
$\kappa>0$ is an assumption about the profile, not a consequence.
\textnormal{(c)} The window \eqref{eq:window} is genuinely open; the
second blow-up of Remark~\ref{rem:window} is a program.
\textnormal{(d)} The intermediate decay range
$0<\varepsilon\le\varepsilon_*$ in branch (ii) remains blocked for the
direct route \textnormal{(}supercritical tails,
Remark~\ref{rem:tail}\textnormal{)}. \textnormal{(e)} Nothing here uses or
proves BDOR-type weighted admissibility of $a_0^h$; the approaches are
complementary and all remain conditional.
\end{remark}

%======================================================================
\section{The conditional growth estimate}\label{sec:growth}
%======================================================================
\begin{definition}[Flat branching point]\label{def:branch}
A point $x_0\in B_1$ is a \emph{flat branching point} of $u$ if $u(x_0)=0$ and
$u$ vanishes to first order at $x_0$, i.e.\ $\sup_{B_r(x_0)}|u|=o(r)$ as
$r\to0$. When $u$ is of class $C^1$ near $x_0$ --- which, for the inhomogeneous
equation, is presently available only conditionally (Remark~\ref{rem:baseline})
--- this is equivalent to $u(x_0)=|Du(x_0)|=0$.
\end{definition}

\begin{assumption}[Compactness and admissibility]\label{ass:compact}
Solutions of \eqref{eq:main} are of class $C^{1+\al'}_{loc}$ for some
$\al'\in(0,\al_0)$, with uniform interior bounds under the normalizations
below \textnormal{(}an inhomogeneous $C^{1,\al'}$ input,
Remark~\ref{rem:baseline}\textnormal{)}. Moreover, whenever amplified blow-ups
$v_k$ (Proposition~\ref{prop:homog}) satisfy $\sup_{B_R}|v_k|\le CR^{\beta}$ for
$1\le R\le c/r_k$ and are nontrivial on $B_1$, a subsequence converges locally
uniformly to an entire $v_0$ whose increments satisfy $L_{K}w_0^h=0$ (the
renormalized limiting equation, Remark~\ref{rem:renorm}), with
$v_0(0)=|Dv_0(0)|=0$, and
$v_0$ admissible for the Liouville step (Lemma~\ref{lem:liouville-cond} or
Theorem~\ref{thm:liouville-incr}, including its hypotheses \textnormal{(ND)}
and $(\star)$).
\end{assumption}

\begin{theorem}[Conditional growth estimate]\label{thm:growth}
Assume the parameter block \eqref{eq:hyp-block} and
Assumption~\ref{ass:compact}. Let $u\in L^\infty(\R^n)$ solve \eqref{eq:main}
with $0$ a flat branching point. Then
\[
  |u(x)|\le C\,|x|^{\beta},\qquad x\in B_{1/2},\qquad C=C(n,s,p,\gamma).
\]
\end{theorem}
\begin{proof}
Fix $\al'\in(0,\min\{\al_0,\beta-1\})$, nonempty since $\beta>1$ and
$\al_0>0$ (here the $C^{1,\al'}$ regularity is part of
Assumption~\ref{ass:compact}). Suppose the estimate fails; then there are
normalized solutions $u_k$ with $u_k(0)=|Du_k(0)|=0$,
$[u_k]_{C^{1+\al'}(B_{1/2})}\le 2C$, and points $x_k$ with
$|u_k(x_k)|>k|x_k|^{\beta}$. With
$\theta_k(r'):=\sup_{r'<r<1/2}r^{1+\al'-\beta}[u_k]_{C^{1+\al'}(B_r)}$
($1+\al'-\beta<0$), the jet-to-growth lemma forces $\theta_k(0^+)>k$; choose
$r_k>1/k$ with
$r_k^{1+\al'-\beta}[u_k]_{C^{1+\al'}(B_{r_k})}\ge\frac1k\theta_k(1/k)\ge
\frac12\theta_k(r_k)$, so $r_k\to0$. Set
$v_k:=u_k(r_k\cdot)/(\theta_k(r_k)r_k^{\beta})$. As in~\cite[(33)]{CP},
$[v_k]_{C^{1+\al'}(B_R)}\le R^{\beta-1-\al'}$ for $1\le R\le\frac1{2r_k}$, and
the gradient-anchor argument gives $|v_k(x)|\le C|x|^{\beta}$ on that range with
$[v_k]_{C^{1+\al'}(B_1)}\ge\frac12$. By Assumption~\ref{ass:compact},
$v_k\to v_0$ locally uniformly, the increments of $v_0$ satisfy $L_K w_0^h=0$
(Remark~\ref{rem:renorm}), $v_0(0)=|Dv_0(0)|=0$,
$|v_0(x)|\le C(1+|x|)^{\beta}$, $[v_0]_{C^{1+\al'}(B_1)}\ge\frac12$. Since
$\beta<1+\asp$ (and $\beta<1+\al_0$), the Liouville step
(Lemma~\ref{lem:liouville-cond}, or Theorem~\ref{thm:liouville-incr} under
\textnormal{(ND)} and $(\star)$) gives $v_0\equiv0$, contradicting the
normalization.
\end{proof}

\begin{remark}
The proof runs the blow-up at the \emph{generic} exponent $\al'$, strictly
below $\al_0$; the sharp exponents enter only through the regularity inputs.
The two genuinely nonlinear-nonlocal difficulties are isolated as
Assumption~\ref{ass:compact} (compactness/tails) and the hypotheses
\textnormal{(ND)}, $(\star)$ of Theorem~\ref{thm:liouville-incr}.
\end{remark}

%======================================================================
\section{Consequences}\label{sec:consequences}
%======================================================================
\begin{corollary}[Gradient growth, conditional]\label{cor:grad}
Under the hypotheses of Theorem~\ref{thm:growth}, and provided the
inhomogeneous $C^{1,\al'}$ bound of Assumption~\ref{ass:compact} is available,
$\sup_{B_r}|Du|\le Cr^{\beta-1}$ for $r<\frac12$.
\end{corollary}

\begin{theorem}[Local limit $s\nearrow1$, conditional]\label{thm:local}
Assume the hypotheses of Theorem~\ref{thm:growth} hold for $s$ near $1$ with
constants uniform in $s$, and let $u$ solve
$\Delta_p u=u_+^\gamma-u_-^\gamma$ in $B_1$ with $0$ a flat branching point.
Then $|u(x)|\le C|x|^{p/(p-1-\gamma)}$ in $B_{1/2}$.
\end{theorem}
\begin{proof}[Proof (sketch)]
As $s\nearrow1$, $\fpl{u}\to-\Delta_p u$ after fixing normalizing constants and
$\beta\to\frac{p}{p-1-\gamma}$; passing to the limit in
Theorem~\ref{thm:growth} gives the claim. The uniformity in $s$ is itself
conditional: the constants of Lemma~\ref{lem:gjs} are \emph{not} uniform as
$s\to1$, so the honest route to the local result is a direct one (the scheme
of~\cite[\S6]{CP} with classical $C^{1,\al}$ theory for $\Delta_p$), to be
carried out separately.
\end{proof}

\subsection{A scale-local barrier}\label{ssec:barrier}
The non-admissibility of $|x|^{\beta}$ as a global profile ($\beta(p-1)>sp$) is,
for barriers, an \emph{advantage}: a power capped far away retains a large
negative tail contribution that fixes the sign of the operator on a fixed
annulus.

\begin{lemma}[Scale-local barrier]\label{lem:barrier}
Let $p\ge2$, $s\in(0,1)$, $0<\gamma<p-1$, $\beta=\frac{sp}{p-1-\gamma}>1$, so
$\beta(p-1)-sp=\beta\gamma>0$. For $L>1$ let $\psi_L:\R^n\to[0,\infty)$ be radial,
nondecreasing in $|x|$, $\psi_L\in C^2(\R^n\setminus\{0\})\cap L^\infty(\R^n)$,
with
\[
  \psi_L(x)=|x|^{\beta}\ (|x|\le2),\qquad \psi_L(x)=L^{\beta}\ (|x|\ge2L),\qquad
  |x|^{\beta}\le\psi_L(x)\le L^{\beta}\ (2\le|x|\le2L),
\]
the interpolation on $\{2<|x|<2L\}$ being smooth and monotone. Write
$Q_L:=\fpl{\psi_L}$, $\mathcal A:=\{1\le|z|\le\tfrac32\}$. Then:
\begin{enumerate}[leftmargin=2.2em]
\item[\textnormal{(i)}] $\fpl{[R^{\beta}\psi_L(\cdot/R)]}(x)=R^{\beta\gamma}\,
  Q_L(x/R)$;
\item[\textnormal{(ii)}] $Q_L$ is finite and continuous on $\mathcal A$, and there
  exist $L_0>1$, $c_0>0$ (depending on $n,s,p,\beta$ and the fixed interpolation)
  with $Q_L(z)\le -c_0<0$ on $\mathcal A$ for all $L\ge L_0$;
\item[\textnormal{(iii)}] hence, with $\psi_{L,R}(x):=R^{\beta}\psi_L(x/R)$,
  \[
    \fpl{\psi_{L,R}}(x)\le -c_0\,R^{\beta\gamma}<0,\qquad R\le|x|\le\tfrac32R .
  \]
\end{enumerate}
\end{lemma}
\begin{proof}
(i) As in Proposition~\ref{prop:scaling}, using $\beta(p-1)-sp=\beta\gamma$.

(ii) Fix $z\in\mathcal A$. Since $z\ne0$, $\psi_L\in C^2$ near $z$ and is
bounded, so the principal value converges; continuity in $z$ follows. Split
$Q_L=Q_{\mathrm{sing}}+Q_{\mathrm{far}}$ with $Q_{\mathrm{sing}}=
\mathrm{P.V.}\!\int_{|y-z|<1/4}$ and $Q_{\mathrm{far}}=\int_{|y-z|\ge1/4}$
(absolutely convergent). For $Q_{\mathrm{sing}}$, both $z\pm\zeta\in B_2$ when
$|\zeta|<\tfrac14$, where $\psi_L=|\cdot|^{\beta}$; symmetrizing
$y=z\pm\zeta$ and using $J_p$ odd,
\[
  Q_{\mathrm{sing}}(z)=-\tfrac{c}{2}\!\int_{|\zeta|<1/4}\!\big[J_p(a_\zeta)+
   J_p(b_\zeta)\big]|\zeta|^{-n-sp}d\zeta,\quad a_\zeta+b_\zeta\ge0,
\]
by convexity of $|z|^{\beta}$ ($\beta>1$); $J_p$ nondecreasing then gives
$J_p(a_\zeta)+J_p(b_\zeta)\ge0$, so $Q_{\mathrm{sing}}(z)\le0$. For
$Q_{\mathrm{far}}$ (no singularity), $\psi_L$ nondecreasing gives
$\psi_L(y)\ge\psi_L(z)$ on $\{|y|>|z|\}$, so $J_p(\psi_L(z)-\psi_L(y))\le0$
there; the only positive part is $\{|y-z|\ge\tfrac14\}\cap\{|y|<|z|\}\subset
B_{3/2}$, where $\psi_L=|\cdot|^{\beta}$ and the kernel is $\le 4^{n+sp}$,
contributing at most $P_1=P_1(n,s,p,\beta)$ \emph{independent of $L$}. On
$\{|y|\ge2L\}$, $\psi_L(y)=L^{\beta}$ and, for $L$ large,
$\psi_L(z)\le(\tfrac32)^{\beta}\le\tfrac12L^{\beta}$, so
\[
  \int_{|y|\ge2L}\!J_p(\psi_L(z)-L^{\beta})\,|z-y|^{-n-sp}dy
  \le -\big(\tfrac12L^{\beta}\big)^{p-1}\!\!\int_{|y|\ge2L}\!|z-y|^{-n-sp}dy
  \le -c_1L^{\beta(p-1)}L^{-sp}=-c_1L^{\beta\gamma}.
\]
Hence $Q_L(z)\le Q_{\mathrm{sing}}+P_1-c_1L^{\beta\gamma}\le P_1-c_1
L^{\beta\gamma}$ uniformly on $\mathcal A$; choosing $L_0$ with $c_1L_0^{\beta
\gamma}\ge P_1+c_0$ gives (ii). (iii) is (i) on $\mathcal A$ rescaled.
\end{proof}

\begin{remark}[Amplitude vs.\ reaction; two-phase caveat]\label{rem:barrier}
For $A>0$, $\fpl{(A\psi_{L,R})}=A^{p-1}\fpl{\psi_{L,R}}$ while
$(A\psi_{L,R})_+^{\gamma}=A^{\gamma}R^{\beta\gamma}\psi_L(\cdot/R)^{\gamma}$;
since $p-1>\gamma$, the operator and reaction terms (both of order
$R^{\beta\gamma}$) are separated by the free factor $A^{p-1-\gamma}$, so
$A\psi_{L,R}$ can be made a super- or sub-solution of \eqref{eq:main} at each
scale. The mechanism of Lemma~\ref{lem:barrier} is that the \emph{non-admissible
tail} of $|x|^{\beta}$, once capped at height $L^{\beta}$, contributes
$\sim -L^{\beta\gamma}\to-\infty$, fixing the sign on the fixed annulus.
\textbf{Two-phase caveat.} The comparison principle for $\fpl{}$ is nonlocal and
requires ordering on the entire complement; $\psi_{L,R}\ge0$ controls the
positive phase only, and (by $u\mapsto-u$) the negative phase. We thus obtain
annular nondegeneracy \emph{within each one-phase region under the comparison
hypotheses}, not across a branching point, where the complement ordering is
delicate --- the open step in route (A) of Section~\ref{sec:open}.
\end{remark}

%======================================================================
\section{Remaining analytic inputs}\label{sec:open}
%======================================================================
The following are unconditional: the scaling identity
(Proposition~\ref{prop:scaling}), the vanishing of the right-hand side along
amplified blow-ups (Proposition~\ref{prop:homog}), the increment linearization
(Proposition~\ref{prop:linincr}), the tail obstruction
(Proposition~\ref{prop:tailobstruction}), and the contradiction scheme modulo
its inputs (Theorem~\ref{thm:growth}). The growth estimate is conditional on
the following, each a concrete analytic statement rather than a black box. We
emphasize that the principal missing ingredient is \emph{not} local regularity
---which is available (Lemma~\ref{lem:gjs})---but \emph{global rigidity for the
degenerate linearized kernel}; items (3) and (4) together with the compactness
of item (1) are the true bottlenecks.
\begin{enumerate}[leftmargin=2em]
\item \emph{Compactness of normalized blow-ups, and the far-field increment
control.} By Proposition~\ref{prop:tailobstruction} the available bounds permit
a divergent tail. Truncation (Lemma~\ref{lem:trunc}) controls the far-field
\emph{oscillation} under $\beta(p-1)<sp+1$ but not its constant; combining
truncation with differencing closes the constant at $p=2$
(Proposition~\ref{prop:p2cancel}) but, for $p\neq2$, the constant $a_k(h)$ is
removed neither by a commutator/cocycle nor by an a posteriori bound
(Proposition~\ref{prop:pneq2}). The precise remaining obstruction is therefore
the \emph{uniform far-field increment control} $a_k(h)\to0$ of
Remark~\ref{rem:farfield}. This last point is \emph{discharged} under a
hypothesis on the exterior data: by Lemma~\ref{lem:exterior}, exterior
$C^{0,\sigma}$ data with $\sigma>\beta(p-1)-sp$ (in particular exterior
Lipschitz data) give $a_k(h)\to0$. So compactness and stability are in place for
solutions with regular exterior data; the obstruction migrates entirely to the
Liouville step.
\item \emph{Control of divergent tails / a stability theorem.} A stability
statement for $\fpl{}$ (resp.\ $L_{K}$) under local uniform convergence with
the appropriate global tail convergence, of the type underlying~\cite{BLS,KKL};
for the constant mode, Lemma~\ref{lem:exterior} suffices under regular exterior
data.
\item \emph{A global, scale-uniform Liouville theorem for the degenerate
linearized kernel} --- the hypothesis $(\star)$ of
Theorem~\ref{thm:liouville-incr}, and the principal remaining problem. The
\emph{local} H\"older estimate is available (\cite[\S7]{GJS,FRO,Serra}, under
uniform ellipticity); the scale-uniform/global form for the \emph{degenerate}
$K_h$ is not. Two structured routes appear more tractable than arbitrary
degeneracy:
\begin{itemize}[leftmargin=2.2em]
\item[(W)] \emph{Weighted-kernel model.} Near a flat point $|Dv(x)|\sim
  |x|^{\beta-1}$, so $K_h$ behaves like the \emph{weighted} kernel
  $\mathcal K(x,y)\sim(|x|+|y|)^{a}|x-y|^{-n-m}$ with $m=sp-p+2$ and
  $a=(\beta-1)(p-2)\ge0$. For $a<n$ (i.e.\ $(\beta-1)(p-2)<n$) the weight
  $|x|^a$ is of Muckenhoupt $A_2$ type; proving H\"older/Liouville estimates
  for this weighted class is a concrete, structured problem replacing
  ``arbitrary degenerate kernel''. This route has recently acquired a solid
  foundation: Behn--Diening--Ok--Rolfes~\cite{BDOR} develop interior H\"older
  continuity and Harnack inequalities (their Theorems 3.4--3.6) for nonlocal
  equations whose kernels are comparable to
  $w(x)w(y)/w(B_{x,y})\cdot|x-y|^{-n}$ with a Muckenhoupt $A_p$ weight $w$ ---
  a nonlocal analogue of Fabes--Kenig--Serapioni, with constants stable as
  $s\nearrow1$. The BDOR framework suggests a possible path to the missing
  Liouville theorem (Hypothesis~\ref{hyp:L}), \emph{provided} one can verify a
  suitable Muckenhoupt-type admissibility condition for the linearized
  coefficient $a_0^h$. We emphasize what is \emph{not} automatic: their
  kernels are point-degenerate of product type, whereas $a_0^h$ is
  pair-degenerate ($a_0^h$ small where $v_0(x)\approx v_0(y)$); their theory
  is stated for the homogeneous equation (they indicate the nonhomogeneous
  extension is expected); and their energy is the $p$-form, while $L_{0,h}$ is
  the linearized quadratic form. Verifying an \emph{averaged} comparability
  $a_0^h(x,y)\gtrsim w(x)^{1/2}w(y)^{1/2}$ with $w\sim|Dv_0|^{p-2}$ in the
  $A_2$ sense --- strictly weaker than pointwise nondegeneracy --- is the
  concrete open problem; the case $n=2$, where $|Du|^{p-2}$ is known to be a
  Muckenhoupt weight for local $p$-harmonic $u$ via quasiregularity of the
  gradient, is the natural first target.
\item[(A)] \emph{Annular nondegeneracy.} If the blow-up limit satisfies
  $|Dv(x)|\sim R^{\beta-1}$ on a large portion of each annulus
  $B_{2R}\setminus B_R$, rescaling the annulus to unit size makes $K_h$
  uniformly elliptic, so the \cite{GJS}-type local estimate applies per annulus
  and the decay argument closes the Liouville. The scale-local barrier
  Lemma~\ref{lem:barrier} ($\fpl{\psi_{L,R}}\le-c_0R^{\beta\gamma}$ on
  $R\le|x|\le\frac32R$) is the tool for this, valid \emph{within one phase};
  establishing annular nondegeneracy \emph{across} a branching point
  (Remark~\ref{rem:barrier}) is the remaining step.
\end{itemize}
\item \emph{Degeneracy of the linearized kernel where $Dv=0$.} The kernel
$K_h$ degenerates at critical points of $v$, in particular at the flat origin
of the blow-up limit (Remark~\ref{rem:order}); hence the nondegeneracy
hypothesis \textnormal{(ND)} must be established for $v_0$, e.g.\ via a barrier
computation for $\fpl{|x|^{\beta}}$, or assumed.
\item \emph{Inhomogeneous $C^1$-regularity / flatness.}
B\"ogelein--Duzaar--Liao--Moring~\cite{BDLM} provide Calder\'on--Zygmund-type
gradient \emph{integrability} ($\nabla u\in L^Q_{loc}$ for all finite $Q$ when
$f\in L^\infty$) and higher differentiability $u\in W^{1+\al,p}_{loc}$, but
\emph{not} an interior $C^{1,\al}$ estimate in general --- the embedding
$W^{1+\al,p}\hookrightarrow C^{1,\sigma}$ requires $\al p>n$. Hence the
$C^1$-flatness gap is \emph{not} closed: the condition $Du(x_0)=0$ in
Definition~\ref{def:branch} remains conditional, and the weaker flatness
$\sup_{B_r}|u|=o(r)$ is the right formulation. A natural intermediate target
is a \emph{perturbation lemma}: since the blow-up right-hand sides satisfy
$f_k\to0$ (Corollary~\ref{cor:incr-weak}), a compactness/improvement-of-
flatness argument against the homogeneous estimate of~\cite{GJS} should yield
uniform interior $C^{1,\al'}$ bounds, $\al'<\al_0$, for solutions with
$\|f\|_{L^\infty}$ small --- weaker than a full inhomogeneous $C^{1,\al}$
theory and plausibly within reach, but \emph{it is another input to prove},
not to cite; it would inherit the restriction $p<\frac{2}{1-s}$ and lose
uniformity as $s\nearrow1$. Until it is proved, the $C^1_{loc}$-compactness
of the blow-ups (Assumption~\ref{ass:compact}) must not be assumed silently.
\item \emph{A modulo-polynomial theory for the degenerate increment kernel.}
The blow-up limit has too large a tail to be $(s,p)$-harmonic in the standard
sense (Remark~\ref{rem:renorm}); the right framework is the polynomial-growth
notion of~\cite{DSV}, in which the equation holds \emph{modulo polynomials} and
the far-field constant $a_k$ (degree $0$) is identified with $0$. This resolves
the constant/stability obstruction for $p=2$ (Remark~\ref{rem:dsv}). For
$p\neq2$ one needs the analogue of~\cite{DSV} for the variable, degenerate,
non-translation-invariant kernel $K_h$, in two pieces:
\begin{itemize}[leftmargin=2.2em]
\item[(i)] a \emph{modulo-polynomial stability} statement: if
  $L_{K_k}\tilde w_k=f_k+a_k+g_k$ on fixed balls with $f_k,g_k\to0$ and $a_k$
  constant, and $K_k\to K_0$, $\tilde w_k\to w_0$ locally with polynomial
  growth, then $L_{K_0}w_0=0$ modulo constants;
\item[(ii)] a \emph{Liouville modulo constants}: if $L_{K_h}w=0$ modulo
  constants in $\R^n$ with $|w(x)|\le C(1+|x|)^{\beta-1}$, $\beta-1<\asp$, then
  $w$ is constant.
\end{itemize}
Neither is supplied by \cite{DSV,FRO,Serra}, which require uniform ellipticity;
the degeneracy of $K_h$ at $\{Dv=0\}$ is the obstruction common to both.
\end{enumerate}

%======================================================================
\section{Conclusion: status of each step}\label{sec:conclusion}
%======================================================================
The table below records the status of every step of the program. ``Rigorous''
means proved in this paper; ``literature'' means used with a precise citation;
``conditional'' means proved here modulo a stated assumption; ``open'' means a
genuinely new statement that must be proved before the main theorem becomes
unconditional.

\begin{center}
\renewcommand{\arraystretch}{1.35}
\begin{tabular}{|p{0.21\textwidth}|p{0.72\textwidth}|}
\hline
\textbf{Rigorous} &
Scaling identity and the exponent $\beta_*=\frac{sp}{p-1-\gamma}$
(Prop.~\ref{prop:scaling}); vanishing right-hand side along amplified
blow-ups (Prop.~\ref{prop:homog}); weak increment identity and
$f_k^h\to0$ (Prop.~\ref{prop:linincr}, Cor.~\ref{cor:incr-weak}); far-field
tail condition $\beta_*(p-1)<sp+1\iff\gamma<\frac{p-1}{1+sp}$, with the
far-field coefficient $\sim|y|^{\beta_*(p-2)}$
(Rem.~\ref{rem:tailcond}); tail obstruction for the normalized sequence
(Prop.~\ref{prop:tailobstruction}); truncation oscillation estimates
(Lem.~\ref{lem:trunc}, \ref{lem:trunc-incr}); constant cancellation at
$p=2$ and its failure mechanisms at $p\neq2$
(Prop.~\ref{prop:p2cancel}, \ref{prop:pneq2}); stability under exterior
H\"older data (Lem.~\ref{lem:exterior}); scale-local barrier
(Lem.~\ref{lem:barrier}); contradiction scheme modulo its inputs
(Thm.~\ref{thm:growth}). \\
\hline
\textbf{Literature} &
Inhomogeneous H\"older/Lipschitz baseline, $p<\frac2{1-s}$~\cite{BT};
homogeneous interior $C^{1,\al_0}$ and local linearized H\"older
estimates~\cite{GJS}; weighted nonlocal
H\"older/Harnack (Fabes--Kenig--Serapioni analogue)~\cite{BDOR};
weak--viscosity equivalence~\cite{KKL}; higher H\"older
machinery~\cite{BLS}; the $p=2$ template~\cite{PTU}. \\
\hline
\textbf{Conditional} &
The growth estimate $|u(x)|\le C|x-x_0|^{\beta_*}$ at flat branching points
(Thm.~\ref{thm:growth}), under Assumption~\ref{ass:compact}
($C^1_{loc}$-compactness of normalized blow-ups) and
Hypothesis~\ref{hyp:L} (degenerate-kernel Liouville); the increment-route
Liouville under \textnormal{(ND)}$+(\star)$
(Thm.~\ref{thm:liouville-incr}); the local limit $s\nearrow1$
(Thm.~\ref{thm:local}). \\
\hline
\textbf{Open} &
Hypothesis~\ref{hyp:L} itself: Liouville for the degenerate linearized
kernel --- equivalently, scale-uniform H\"older/Harnack for $L_{0,h}$; the
Muckenhoupt/BDOR admissibility of $a_0^h$ (route (W), \S\ref{sec:open});
the perturbation lemma (uniform $C^{1,\al'}$ for small right-hand side);
annular nondegeneracy across a two-phase branching point; sharpness of
$\gamma<\frac{p-1}{1+sp}$. \\
\hline
\end{tabular}
\end{center}

\medskip
\noindent\textbf{Safe statement.} The theorem this paper proves is
Theorem~\ref{thm:growth}: \emph{for $p\ge2$, $p<\frac2{1-s}$,
$0<\gamma<\frac{p-1}{1+sp}$, if $u$ is a bounded weak solution of
\eqref{eq:main} and $x_0$ is a flat branching point in the sup sense, then,
under Assumption~\ref{ass:compact} and Hypothesis~\ref{hyp:L},
$|u(x)|\le C|x-x_0|^{\beta_*}$ near $x_0$.} No unconditional claim is made,
and no pointwise gradient condition at $x_0$ is used.

%======================================================================
\begin{thebibliography}{9}
\bibitem{BDLM} V. B\"ogelein, F. Duzaar, N. Liao, S. Moring, \emph{Gradient
estimates for the fractional $p$-Poisson equation}. % details to verify before submission
\bibitem{BDOR} L. Behn, L. Diening, J. Ok, J. Rolfes, \emph{Nonlocal
equations with degenerate weights}, preprint arXiv:2409.11829.
\bibitem{BT} A. Biswas, E. Topp, \emph{Lipschitz regularity of fractional
$p$-Laplacian}, Ann. PDE 11 (2025), no.~2, Paper No.~27.
\bibitem{BLS} L. Brasco, E. Lindgren, A. Schikorra, \emph{Higher H\"older
regularity for the fractional $p$-Laplacian in the superquadratic case},
Adv. Math. 338 (2018), 782--846.
\bibitem{CP} J.C. Correa, D. dos Prazeres, \emph{A two-phase quenching-type
problem for the $p$-Laplacian}, preprint arXiv:2504.11370.
\bibitem{CSapprox} L. Caffarelli, L. Silvestre, \emph{Regularity results for
nonlocal equations by approximation}, Arch. Ration. Mech. Anal. 200 (2011),
59--88.
\bibitem{DSV} S. Dipierro, O. Savin, E. Valdinoci, \emph{Definition of
fractional Laplacian for functions with polynomial growth}, Rev. Mat.
Iberoam. 35 (2019), no.~4, 1079--1122; arXiv:1610.04663.
\bibitem{FRO} X. Fern\'andez-Real, X. Ros-Oton, \emph{Schauder and
Cordes--Nirenberg estimates for nonlocal elliptic equations with singular
kernels}, preprint arXiv:2308.11383.
\bibitem{Serra} J. Serra, \emph{$C^{\sigma+\alpha}$ regularity for concave
nonlocal fully nonlinear elliptic equations with rough kernels}, Calc. Var.
Partial Differential Equations 54 (2015), 3571--3601; arXiv:1405.0930.
\bibitem{GJS} D. Giovagnoli, D. Jesus, L. Silvestre, \emph{$C^{1+\alpha}$
regularity for fractional $p$-harmonic functions}, preprint arXiv:2509.26565.
\bibitem{KKL} J. Korvenp\"a\"a, T. Kuusi, E. Lindgren, \emph{Equivalence of
solutions to fractional $p$-Laplace type equations}, J. Math. Pures Appl.
132 (2019), 1--26.
\bibitem{PTU} D. dos Prazeres, R. Teymurazyan, J.M. Urbano, \emph{Improved
regularity for a nonlocal dead-core problem}, arXiv:2504.09557, to appear in
Indiana Univ. Math. J.
\end{thebibliography}
\end{document}
